\documentclass[11pt]{amsart}
\input{preamble}

\title[Bounds and Barriers for Erd\H{o}s Problem 872]{Improved Bounds and Proof-Class Barriers for the Divisibility Antichain Saturation Game (Erd\H{o}s Problem 872)}

\author{Om Buddhdev}
\address{Independent Researcher}
\email{\href{mailto:sensho@sensho.xyz}{sensho@sensho.xyz}}

\date{April 21, 2026}

\subjclass[2020]{Primary 91A46; Secondary 05D05, 11N25}
\keywords{Saturation game, primitive set, divisibility poset, antichain, sieve methods, formal verification, Erd\H{o}s problem 872}

\begin{document}

\begin{abstract}
Erd\H{o}s posed the divisibility antichain saturation game on
$\{2,3,\ldots,n\}$ in 1992 \cite{Er92c}, catalogued as Problem~\#872 in
Bloom's list \cite{Bloom872}.  Two players alternately choose integers,
maintaining the property that the chosen set is primitive (an antichain
under divisibility); Prolonger moves first to maximize the final count,
Shortener moves to minimize it.  The central question is whether the game
value $\L(n)$ is linear in $n$ or sublinear.  We prove
\[
  \left(\frac18-o(1)\right)\frac{n\log\log n}{\log n}
  \;\le\;
  \L(n)
  \;\le\;
  \left(\frac{\Wfour}{2}+o(1)\right)n
  \;<\;0.19\,n,
\]
where $\Wfour$ is an explicit fourth-order Bonferroni constant arising from
the local logarithmic density of Shortener's legal-prime prefix.  The lower
bound follows from a two-phase Prolonger strategy and a bipartite
maximum-degree capture lemma; the upper bound uses a monotone envelope for
the legal-prime density, a queued prime-rounding bridge, and a fourth-order
Bonferroni inequality on the odd-part compression of the terminal antichain.
We also prove a polynomial lower bound for the weighted shield functional,
an exact $5n/24+O(1)$ first-hit cover theorem for the lower half, and
intermediate asymptotic upper-bound constants $13/36$ and $5/16$.  A conditional
lower bound of order $n(\log\log n)^2/\log n$ is included under an explicit
finite safe-edge hypothesis.  The paper also records three structural
barriers limiting related proof methods.
\end{abstract}

\maketitle

\input{sections/01-introduction}
\input{sections/02-notation-and-setup}
\input{sections/03-shield-reduction}
\input{sections/04-lower-bounds}
\input{sections/05-524-cover}
\input{sections/06-intermediate-upper-bounds}
\input{sections/07-main-upper-bound}
\input{sections/08-obstructions}
\input{sections/09-conclusion}

\appendix
\input{sections/appendix-A-deferred-proofs}
\input{sections/appendix-B-numerical}
\input{sections/appendix-C-formalization}

\section*{Artifact Availability}

\begin{sloppypar}
The public artifact repository for this paper is available at
\url{https://github.com/xa8zz/erdos-harness}; the version corresponding to
this submission is tagged \texttt{arxiv-v1} in the repository, and
\cite{ErdosHarness26} records the artifact metadata.  It contains the Lean formalizations, Aristotle submission files
and outputs, numerical scripts, and supporting research notes used in the
preparation of the present manuscript.  Repository-relative paths quoted in
\Cref{app:numerical,app:formalization} are relative to that artifact root.
\end{sloppypar}

\section*{Acknowledgments}

The author thanks Liam Price, Abhimanyu Adenwalla, StijnC, natso26, Xiao\_Hu,
and Desmond Weisenberg for the forum refinement chain leading from the first
linear bound to the previous public record, and Thomas Bloom for maintaining
\texttt{erdosproblems.com}.  The author also wishes to record substantial
gratitude for the research assistance provided by OpenAI's GPT-5.4 Pro,
Anthropic's Claude Opus 4.7, and Google's Gemini 3.1 DeepThink, coordinated
through a custom multi-round research harness built by the author.  GPT-5.4 Pro
produced the majority of the exploratory mathematical output used in this
project, with Claude and Gemini providing extensive auditing, synthesis, and
drafting support.  A separate methodological paper and public-facing writeup
will describe that workflow in detail.

\section*{Declaration of Generative AI and AI-assisted Technologies in the Research and Writing Process}

During the preparation of this work, the mathematical content was produced
primarily by generative AI systems---OpenAI GPT-5.4 Pro, Anthropic Claude
Opus 4.7, and Google Gemini 3.1 DeepThink---coordinated through a custom
multi-round research harness designed and operated by the author.  GPT-5.4 Pro
generated the majority of the novel mathematical arguments, including the
shield reduction, the polynomial shield barrier, the Round~15 piecewise-density
analysis, and the barrier taxonomy.  Claude Opus~4.7 and Gemini~3.1 DeepThink
provided adversarial auditing, cross-model verification, synthesis across
rounds, and drafting support.  The author's contributions were the harness
design, problem selection and scoping, round-by-round direction and
adversarial prompting, selection and integration of outputs into a coherent
manuscript, Lean/Aristotle formalization work, numerical verification, and
final writing.  The author takes full responsibility for the correctness of
the claims, the validity of the proofs as presented, the accuracy of the
citations, and the integrity of the formal artifacts.  A description of the
harness and workflow is available at~\url{https://www.sensho.xyz/autonomous-research}.

\bibliographystyle{amsalpha}
\bibliography{references}

\end{document}
