\section{Introduction}\label{sec:introduction}

Let $n\ge 2$.  The divisibility antichain saturation game is played on
\[
  \{2,3,\ldots,n\}.
\]
Two players alternately choose previously unchosen integers, and the chosen set
must remain an antichain under divisibility.  Thus no chosen integer may divide
another chosen integer.  The game stops when the current antichain is maximal.
Prolonger moves first and tries to maximize the final number of chosen
integers; Shortener tries to minimize it.  We denote the value of the game by
$\L(n)$.

This game is one of the finite saturation games arising from Erd\H{o}s's
questions on primitive sets \cite{Er92c}; saturation games of this kind are
part of a broader extremal-game tradition \cite{FuSe91,BPW16}.  A primitive set
is precisely an antichain in the divisibility poset, and primitive sets have a
long parallel history in multiplicative number theory
\cite{CaEr90,Lichtman23,MartinPomerance10,Kucheriaviy24}.  The upper half
\[
  \U_n:=\{m:\ n/2<m\le n\}
\]
is the canonical maximum antichain, so the trivial scale is linear.  The
central question is whether optimal play forces a positive fraction of this
linear scale, or whether Shortener can force $o(n)$ moves.

\subsection{Prior work}

Erd\H{o}s posed the problem in 1992 \cite{Er92c}, and it is catalogued as
problem \#872 in Bloom's list \cite{Bloom872}.  No non-trivial upper bound
appeared in the public record until early 2026.  The game is a
number-theoretic analogue of the triangle-free saturation game of Hajnal:
for that game, F{\"u}redi and Seress \cite{FuSe91} proved a lower bound of
order $n\log n$, while Bir{\'o}, Horn, and Wildstrom \cite{BPW16} proved an
upper bound below $0.215n^2$.

The ambient combinatorial setting interacts with the literature on primitive
sets and divisibility antichains.  We use the primitive-set viewpoint of
Cameron and Erd\H{o}s \cite{CaEr90}, the weighted extremal perspective from
Lichtman's proof of the Erd\H{o}s primitive set conjecture \cite{Lichtman23},
and supporting multiplicative-structure estimates from
\cite{Kucheriaviy24,MartinPomerance10}.

The public upper-bound record for the present game developed rapidly in early
2026.  Price and GPT-5.2 Pro gave the first linear upper bound,
\[
  \L(n) \le \left(\tfrac{23}{48}+o(1)\right)n,
\]
and introduced the terminology \emph{Prolonger} and \emph{Shortener}
\cite{PriceGPTPro26}.  Subsequent forum refinements by Adenwalla, StijnC,
natso26, Xiao\_Hu, Desmond Weisenberg, and others improved this to
\[
  \L(n) \le \left(\tfrac{419}{1008}+o(1)\right)n \le 0.416n
\]
\cite{Forum872}.  The results in this paper substantially strengthen that
record and add the first unconditional nontrivial lower bound.

\subsection{Main results}

Our main result is a new linear upper bound with an explicit constant below
$0.19$.  Let
\[
  \rho(u):=\frac{1}{(\lfloor 1/u\rfloor+1)u}\qquad(0<u\le 1),
\]
and define
\[
  J_r:=
  \frac1{r!}
  \int_{\substack{u_1+\cdots+u_r\le1\\0<u_i\le1}}
  \prod_{i=1}^r \rho(u_i)\,du_1\cdots du_r
  \qquad (r\ge1).
\]
Set
\[
  \Wfour:=1-J_1+J_2-J_3+J_4.
\]
The certified numerical bound in \Cref{prop:wfour-certification} is
\[
  \frac{\Wfour}{2}\le0.1897123371<0.19.
\]

\begin{theorem}[Main upper bound]\label{thm:intro-main}
Shortener has a strategy forcing
\[
  \L(n)\le \left(\frac{\Wfour}{2}+o(1)\right)n<0.19n.
\]
\end{theorem}

The proof of \Cref{thm:intro-main} is given in \Cref{sec:main-upper}.  Shortener
plays a long prefix of the smallest legal odd primes.  The local law governing
which primes can be kept legal has density $\rho(u)$ on the logarithmic scale
$p=n^u$.  We build a monotone envelope for this density, invert it to obtain a
comparison sequence, round the comparison sequence to genuine primes without
losing the first four factorial moments, and then apply a fourth-order
Bonferroni inequality to the odd-part compression of the final antichain.

\begin{theorem}[Unconditional fan lower bound]\label{thm:intro-lower-bound}
Prolonger has a strategy forcing
\[
  \L(n)\ge
  \left(\frac18-o(1)\right)\frac{n\log\log n}{\log n}.
\]
\end{theorem}

The proof of \Cref{thm:intro-lower-bound} is given in
\Cref{thm:fan-lower-bound}.  Prolonger first works through the small odd primes
$a\le n^\delta$, making them unavailable by legal upper-half multiples unless
Shortener chooses the singleton first.  A harmonic charging argument shows that
the small primes made unavailable by proper multiples still have reciprocal
mass at least half of the total small-prime mass.  The remaining upper-half
targets $ab$ form a fan graph, and a maximum-degree right-capture lemma forces
at least half of the surviving fan edges to become actual game moves.

The lower-bound side also contains a weighted obstruction theorem for the
standard shield-reduction approach.  For $x\le n/2$, let
\[
  M_n(x):=\{u\in\U_n:\ x\mid u\},\qquad
  w_n(x):=|M_n(x)|-1.
\]
For $P\subseteq\U_n$, put
\[
  \mathcal L_n(P):=\{x\le n/2:\ x\nmid u\ \text{for every }u\in P\},
\]
and let
\[
  \beta_n(P):=\max\left\{\sum_{x\in B}w_n(x):
    B\subseteq\mathcal L_n(P)\ \text{is a divisibility antichain}\right\}.
\]

\begin{theorem}[Polynomial shield-weight lower bound]\label{thm:intro-A}
Fix $0<\alpha<1$.  Uniformly for every $P\subseteq\U_n$ with
$|P|\le n^\alpha$,
\[
  \beta_n(P)\ge
  \left(\frac12\log\frac1\alpha-o(1)\right)n.
\]
Equivalently, if
\[
  k_c^\star(n):=\min\{|P|:\ P\subseteq\U_n,\ \beta_n(P)\le cn\},
\]
then for every fixed $c>0$,
\[
  k_c^\star(n)\ge n^{e^{-2c}-o(1)}.
\]
\end{theorem}

The next theorem explains why this weighted quantity is the right one for
shield-prefix arguments.

\begin{theorem}[Shield reduction framework]\label{thm:intro-shield}
Let $A$ be any terminal antichain and let $P\subseteq A\cap \U_n$.  Then
\[
  |A|\ge |\U_n|-\beta_n(P).
\]
Consequently, any proof which uses a prefix $P\subseteq\U_n$ and this reduction
to force $|A|\ge (1/2-c)n+o(n)$ must have
\[
  |P|\ge n^{e^{-2c}-o(1)}.
\]
\end{theorem}

The proof of the reduction is elementary and is given in \Cref{sec:shield};
\Cref{thm:intro-A} is proved in \Cref{sec:lower-bounds}.  These structural
results show that a short upper-half shield prefix cannot certify a linear
lower bound through the weighted shadow method.

We also determine exactly the size of the first-hit cover of the lower half by
upper-half multiples.  Define
\[
  \tau(n):=\min\{|C|:\ C\subseteq\U_n,\ \forall x\in L_n\ \exists u\in C
  \text{ with }x\mid u\}.
\]

\begin{theorem}[Exact first-hit cover]\label{thm:intro-cover}
\[
  \tau(n)=\frac{5}{24}n+O(1).
\]
More precisely, the cover
\[
  H_n=\{u\in\U_n:\ u\equiv2\pmod4\}
  \cup
  \{u\in\U_n:\ u>2n/3,\ u\equiv0\pmod4\}
\]
has size $5n/24+O(1)$, and there is a matching packing of lower-half
witnesses of the same size up to $O(1)$.
\end{theorem}

Before the fourth-order argument, the same prime-prefix method gives two
simpler upper bounds.

\begin{theorem}[Intermediate upper bounds]\label{thm:intro-intermediate}
Shortener has explicit strategies forcing
\[
  \L(n)\le \left(\frac{13}{36}+o(1)\right)n
\]
and
\[
  \L(n)\le \left(\frac{5}{16}+o(1)\right)n.
\]
\end{theorem}

Finally, we include a conditional lower-bound theorem, not as a headline
result but as a useful finite-combinatorial target.  The natural general
safe-edge hypothesis is false even inside the arithmetic residual hypergraphs,
so the theorem is conditional on a narrower hypothesis for states generated by
the activation and residual strategies in \Cref{sec:lower-bounds}.  Under that
restricted hypothesis, the residual slot construction gives
\[
  \L(n)\ge c\,\frac{n(\log\log n)^2}{\log n}
\]
for some absolute $c>0$.  The finite graph, hypergraph, and arithmetic
embedding cores of this theorem are formally verified; the restricted
safe-edge hypothesis and the asymptotic activation wrapper remain in prose and
are stated explicitly rather than suppressed.

Several parts of the paper are accompanied by Lean formalizations.  The Shield
Reduction theorem, the structural identities underlying the exact $5/24$ cover,
and the $13/36$ upper-bound core have zero-sorry Lean verifications.  Theorem A
and the $5/16$ upper bound have Lean artifacts whose remaining sorries are
standard analytic-number-theory inputs or their assembly.  The finite
graph/hypergraph/embedding cores of the conditional T2 theorem are
Lean-verified, while the restricted safe-edge hypothesis and asymptotic wrapper
remain prose.  For the $0.19n$ theorem, the endgame reduction from moment
convergence to the strict inequality is zero-sorry Lean-verified; the
moment-convergence hypotheses are the prose content of \Cref{sec:main-upper}.
A full status table appears in \Cref{app:formalization}.

The paper is organized as follows.  \Cref{sec:notation} fixes notation.
\Cref{sec:shield} proves the shield reduction.  \Cref{sec:lower-bounds} proves
Theorem A, the unconditional fan lower bound, and states the conditional T2
theorem.  \Cref{sec:cover} proves the $5/24$ cover theorem.
\Cref{sec:intermediate} proves the $13/36$ and $5/16$ upper bounds.
\Cref{sec:main-upper} proves the main $0.19n$ bound.  \Cref{sec:obstructions}
records three obstructions to extending the present methods.  Deferred proofs,
numerical details, and formalization metadata appear in the appendices.
