\section{Lower Bounds and Conditional Slot Construction}\label{sec:lower-bounds}

This section proves the polynomial shield-weight obstruction and an
unconditional fan-capture lower bound for the game, and then states the
conditional T2 lower bound.  The conditional result is deferred to
\Cref{app:deferred-proofs}.

\subsection{The polynomial shield-weight lower bound}

\begin{theorem}[Polynomial shield-weight lower bound]\label{thm:theorem-A}
Fix $0<\alpha<1$.  Uniformly over all $P\subseteq\U_n$ with $|P|\le n^\alpha$,
\[
  \beta_n(P)\ge
  \left(\frac12\log\frac1\alpha-o(1)\right)n.
\]
\end{theorem}

\begin{proof}
Fix $\delta$ with $\alpha<\delta<1$.  Let
\[
  Q_\delta(P):=
  \{p\le n^\delta:\ p\ \text{prime and }p\nmid u\text{ for every }u\in P\}.
\]
Here and below, we use the Prime Number Theorem
\cite[Theorem~6]{HardyWright08} and its fixed-ratio interval form.
For all sufficiently large $n$, every $p\le n^\delta$ lies in $L_n$.  The set
$Q_\delta(P)$ is an antichain and is contained in $\mathcal L_n(P)$, so
\[
  \beta_n(P)\ge \sum_{p\in Q_\delta(P)}w_n(p).
  \tag{4.1}\label{eq:A-start}
\]
For $p\le n^\delta$,
\[
  w_n(p)
  =
  \left\lfloor\frac np\right\rfloor
  -
  \left\lfloor\frac{n}{2p}\right\rfloor
  -1
  =
  \frac{n}{2p}+O(1).
\]
Since $\pi(n^\delta)=o(n)$, \eqref{eq:A-start} gives
\[
  \beta_n(P)
  \ge
  \frac n2\sum_{p\in Q_\delta(P)}\frac1p-o(n).
  \tag{4.2}\label{eq:A-weight}
\]

Let
\[
  C_\delta(P):=\{p\le n^\delta:\ p\ \text{prime and }p\mid u
  \text{ for some }u\in P\}.
\]
Then $Q_\delta(P)$ and $C_\delta(P)$ partition the primes up to $n^\delta$.

We first bound the reciprocal mass of $C_\delta(P)$.  For each
$p\in C_\delta(P)$ choose one $u(p)\in P$ divisible by $p$.  For any fixed
$u\in P$, the primes assigned to $u$ are distinct divisors of $u$, so
\[
  \sum_{p:\,u(p)=u}\log p\le \log u\le \log n.
\]
Summing over $u\in P$ gives
\[
  \sum_{p\in C_\delta(P)}\log p\le |P|\log n\le n^\alpha\log n.
  \tag{4.3}\label{eq:log-budget}
\]
Among all finite prime sets satisfying a log-budget
$\sum_{p\in S}\log p\le B$, the reciprocal sum $\sum_{p\in S}1/p$ is maximized
by taking the smallest primes first.  Indeed, if $S$ contains a prime $q$ and
omits a smaller prime $p<q$, then replacing $q$ by $p$ decreases the log-cost
and increases the reciprocal sum.  Iterating this exchange proves the claim.

Let $z_n$ be the largest value for which
\[
  \vartheta(z_n)=\sum_{p\le z_n}\log p\le n^\alpha\log n.
\]
By \eqref{eq:log-budget} and the exchange argument,
\[
  \sum_{p\in C_\delta(P)}\frac1p
  \le
  \sum_{p\le z_n}\frac1p.
  \tag{4.4}\label{eq:covered-mertens-bound}
\]
Chebyshev's theorem $\vartheta(x)\sim x$
\cite[Theorem~7]{HardyWright08} gives
\[
  z_n=(1+o(1))n^\alpha\log n,
\]
and hence
\[
  \log\log z_n=\log\log n+\log\alpha+o(1).
\]
Mertens' theorem for primes \cite{HardyWright08} yields
\[
\begin{aligned}
  \sum_{p\in Q_\delta(P)}\frac1p
  &=
  \sum_{p\le n^\delta}\frac1p
  -
  \sum_{p\in C_\delta(P)}\frac1p\\
  &\ge
  \sum_{p\le n^\delta}\frac1p
  -
  \sum_{p\le z_n}\frac1p\\
  &=
  \log\log(n^\delta)-\log\log z_n+o(1)\\
  &=
  \log\frac{\delta}{\alpha}+o(1).
\end{aligned}
\]
Substituting this into \eqref{eq:A-weight} gives
\[
  \beta_n(P)\ge
  \left(\frac12\log\frac{\delta}{\alpha}-o(1)\right)n.
\]
Letting $\delta\uparrow1$ proves the theorem.
\end{proof}

\begin{corollary}[Barrier exponent]\label{cor:barrier-exponent}
For every fixed $c>0$,
\[
  k_c^\star(n)
  :=
  \min\{|P|:\ P\subseteq\U_n,\ \beta_n(P)\le cn\}
  \ge n^{e^{-2c}-o(1)}.
\]
\end{corollary}

\begin{proof}
If $|P|\le n^\alpha$ and $\beta_n(P)\le cn$, then
\Cref{thm:theorem-A} gives
\[
  \frac12\log\frac1\alpha\le c+o(1).
\]
Thus $\alpha\ge e^{-2c}-o(1)$, which is the claimed exponent lower bound.
\end{proof}

\subsection{An unconditional fan-capture lower bound}

The trivial unconditional lower bound for the game is
$\L(n)\ge(1+o(1))n/\log n$: in any maximal primitive subset
$A\subseteq\{2,\ldots,n\}$, maximality forces $A$ to contain, for each prime
$p\in(\sqrt n,n]$, some multiple of $p$; and two distinct primes in
$(\sqrt n,n]$ have no common multiple in $\{2,\ldots,n\}$, giving
$|A|\ge\pi(n)-\pi(\sqrt n)\sim n/\log n$ \cite{Forum872}.  The theorem below
improves this baseline by a factor of order $\log\log n$, giving the first
unconditional lower bound of strictly larger order.

The shield obstruction above does not itself give a game lower bound.  We now
record a direct unconditional lower-bound strategy for Prolonger.  The
mechanism is different: Prolonger first makes a large reciprocal-mass set of
small primes unavailable, then uses the resulting fan graph of upper-half
products.

\begin{lemma}[Maximum-degree right capture]\label{lem:max-degree-capture}
Let $G=(L\sqcup R,E)$ be a finite bipartite graph.  Consider the following
finite capture game on the live graph.  Maker moves first.  On each Maker move,
Maker chooses a right vertex of maximum positive live degree, captures all
currently live edges incident to it, and removes that right vertex and its
incident live edges.  On each Breaker move, Breaker may delete one right vertex
and all live edges incident to it, delete one live edge, or do nothing.  The
game stops when no live edge remains.

Let $C$ be the number of edges captured by Maker, and let $X$ be the number of
edges individually deleted by Breaker.  Then, regardless of Breaker's play,
\[
  C+X\ge \frac{|E|}{2}.
\]
\end{lemma}

\begin{proof}
Index Maker's nontrivial moves by $i$.  Let $d_i$ be the live degree of the
right vertex captured by Maker on move $i$.  Thus this move contributes $d_i$
to $C$.  Since Maker chose a maximum-degree right vertex, after Maker removes
it every remaining right vertex has live degree at most $d_i$.  Therefore, if
Breaker replies by deleting a right vertex in the same round, that deletion
removes at most $d_i$ live edges.  If Breaker instead deletes one edge or does
nothing, the number of right-deleted edges in that round is $0$.

Let $D_{\mathrm{right}}$ be the total number of edges deleted through
right-vertex deletions.  Summing the preceding round-by-round bound gives
\[
  D_{\mathrm{right}}\le \sum_i d_i=C.
\]
Every original edge is eventually in exactly one of three classes: captured by
Maker, deleted as part of a right-vertex deletion, or individually deleted by
Breaker.  Hence
\[
  |E|=C+D_{\mathrm{right}}+X\le 2C+X\le 2(C+X),
\]
which proves the claim.
\end{proof}

\begin{theorem}[Unconditional fan-capture lower bound]\label{thm:fan-lower-bound}
For every fixed $0<\delta<1/2$ and every $\eps>0$, for all sufficiently large
$n$, Prolonger has a strategy forcing
\[
  \L(n)\ge
  \left(\frac18-\eps\right)\frac{n\log\log n}{\log n}.
\]
Equivalently,
\[
  \L(n)\ge
  \left(\frac18-o(1)\right)\frac{n\log\log n}{\log n}.
\]
\end{theorem}

\begin{proof}
Fix $0<\delta<1/2$ and put $y:=n^\delta$.  Let
\[
  \mathcal A:=\{a\le y:\ a\in\PP,\ a\text{ odd}\}.
\]
For each $a\in\mathcal A$, define the right-prime interval
\[
  J_a:=\left(\frac{n}{2a},\frac na\right]\cap\PP.
\]
If $b\in J_a$, then $ab\in\U_n$.  Also $b>y$ for all sufficiently large $n$,
because $b>n/(2y)=\frac12n^{1-\delta}$ and $\delta<1/2$.

We shall use the fan graph with left vertices in $\mathcal A$, right vertices
the primes appearing in the intervals $J_a$, and edges $(a,b)$ representing the
upper-half target $ab$.

\smallskip
\noindent\emph{Phase 1: activating small primes.}
As long as some prime in $\mathcal A$ is still a legal singleton at the start
of a Prolonger turn, Prolonger takes the smallest such prime $a$ and plays a
legal target $ab$ with $b\in J_a$.  Such a target exists.  Indeed, before any
Phase~1 Prolonger move there have been $O(|\mathcal A|)$ previous Phase~1
moves, while uniformly for $a\in\mathcal A$ the prime number theorem gives
\[
  |J_a|
  =
  (1+o_\delta(1))\frac{n}{2a\log(n/a)}
  \gg_\delta
  \frac{n^{1-\delta}}{\log n}.
\]
This is larger than $|\mathcal A|=O_\delta(n^\delta/\log n)$ because
$\delta<1/2$.  If $a$ is still legal, a previously chosen number can make a
candidate $ab$ illegal only by being $b$ itself or $ab$ itself; each previous
move rules out at most one candidate $b$.  Therefore some legal $ab$ remains.

Phase~1 ends when no prime in $\mathcal A$ is a legal singleton.  If this
happens immediately after a Prolonger move, include Shortener's next move, if
there is one, in the Phase~1 damage accounting below before Phase~2 starts.
This convention only adds one Shortener move.

Define
\[
  A_0:=\{a\in\mathcal A:\text{ during Phase~1, }a\text{ is made illegal by a
  chosen proper multiple}\}
\]
and
\[
  \mathcal D:=\{a\in\mathcal A:\text{ Shortener chooses the singleton }a
  \text{ during Phase~1}\}.
\]
Prolonger never plays a singleton from $\mathcal A$, and a prime singleton can
become illegal only by being chosen itself or by having a proper multiple
chosen.  Thus
\[
  \mathcal A=A_0\sqcup\mathcal D.
\]

Let $P\subseteq A_0$ be the set of primes activated by Prolonger's Phase~1
moves.  Pair each $a'\in\mathcal D$ with the immediately preceding Prolonger
activation $a\in P$.  The pairs are distinct because turns alternate.  Since
Prolonger always activates the smallest currently live prime, and since
legality only decreases as play proceeds, $a\le a'$.  Therefore
\[
  \sum_{a'\in\mathcal D}\frac1{a'}
  \le
  \sum_{a\in P}\frac1a
  \le
  \sum_{a\in A_0}\frac1a.
\]
Using $\mathcal A=A_0\sqcup\mathcal D$ and Mertens' theorem for primes,
\[
  \sum_{a\in A_0}\frac1a
  \ge
  \frac12\sum_{a\in\mathcal A}\frac1a
  =
  \left(\frac12-o(1)\right)\log\log n.
  \tag{4.5}\label{eq:fan-A0-mass}
\]

\smallskip
\noindent\emph{Phase 1 damage and the surviving fan.}
Let $E^\star$ be the raw fan-edge set over $A_0$:
\[
  E^\star:=\{(a,b):a\in A_0,\ b\in J_a\}.
\]
The same uniform prime number theorem estimate gives
\[
\begin{aligned}
  |E^\star|
  &=
  \sum_{a\in A_0}|J_a|\\
  &\ge
  \left(\frac12-o_\delta(1)\right)
  \frac n{\log n}
  \sum_{a\in A_0}\frac1a\\
  &\ge
  \left(\frac14-o_\delta(1)\right)
  \frac{n\log\log n}{\log n},
\end{aligned}
  \tag{4.6}\label{eq:raw-fan-count}
\]
by \eqref{eq:fan-A0-mass}.

We now remove from $E^\star$ the edges whose targets have already become
unavailable before the first Phase~2 Prolonger move, and call the remaining
edge set $E_0$.  If $a\in A_0$, the singleton $a$ was not chosen.  Since
$ab>n/2$, the target $ab$ has no proper multiple in $\{2,\ldots,n\}$, and its
only relevant proper divisors are $a$ and $b$.  Hence a Phase~1 move can
destroy a raw fan edge $(a,b)$ only by choosing the right singleton $b$, which
removes a whole right star, or by choosing the exact target $ab$, which removes
one edge.

There are $O(|\mathcal A|)$ Phase~1 moves, including the possible intervening
Shortener move.  Right-singleton choices therefore destroy at most
$O(|\mathcal A|^2)$ raw fan edges, and exact-target choices destroy at most
$O(|\mathcal A|)$ raw fan edges.  Since
\[
  |\mathcal A|=O_\delta\!\left(\frac{n^\delta}{\log n}\right),
\]
the total damage is
\[
  O_\delta\!\left(\frac{n^{2\delta}}{\log^2 n}\right)
  =
  o_\delta\!\left(\frac n{\log n}\right)
  =
  o_\delta\!\left(\frac{n\log\log n}{\log n}\right).
\]
Consequently
\[
  |E_0|
  \ge
  \left(\frac14-o_\delta(1)\right)
  \frac{n\log\log n}{\log n}.
  \tag{4.7}\label{eq:surviving-fan-count}
\]

\smallskip
\noindent\emph{Phase 2: capturing right stars.}
On the surviving fan graph $G_0=(A_0\sqcup R_0,E_0)$, Prolonger follows the
maximum-degree right-capture strategy from \Cref{lem:max-degree-capture}.  That
is, on each Phase~2 turn he chooses a right prime $b$ of maximum positive
current degree and plays one legal target $a_0b$ incident to it.

This move is legal.  The left singleton $a_0$ is already illegal from Phase~1,
but it was not chosen; the right singleton $b$ has not been chosen, because
otherwise the whole right star would have been removed from $E_0$; and the
target $a_0b$ itself is still available by the definition of $E_0$.  Since
$a_0b>n/2$, no proper multiple of it is on the board, and the only relevant
proper divisors are $a_0$ and $b$.

Shortener's reply has one of the three effects allowed in
\Cref{lem:max-degree-capture}: choosing a right singleton deletes a right
vertex and its live star; choosing an exact fan target $ab$ deletes that one
live edge if it is still live, and is a do-nothing move relative to the live
graph if $ab$ was already captured in an earlier right-star capture by
Prolonger; any other legal move deletes no live fan edge.  Therefore the lemma applies.
Let $C$ be the number of fan edges captured by Prolonger's right-star moves in
Phase~2, and let $X$ be the number of live fan edges individually deleted by
Shortener as exact targets in Phase~2.  Then
\[
  C+X\ge \frac{|E_0|}{2}.
  \tag{4.8}\label{eq:fan-capture-half}
\]

It remains to translate captured graph edges back to actual game moves.  When
Prolonger captures a right prime $b$ by playing some $a_0b$, the capture-move
edge $(a_0,b)$ is realized as Prolonger's current game move.  For every
\emph{other} edge $(a,b)$ live at that capture time, with $a\ne a_0$, the
singleton $a$ is already illegal from Phase~1 but was not chosen, and the
target $ab$ has not yet been chosen.  Moreover $ab$ has no proper multiple in
$\{2,\ldots,n\}$ and its only relevant proper divisors are $a$ and $b$; any
proper multiple of $a$ that was chosen in Phase~1 is not comparable with this
surviving target.  Therefore $ab$ remains legal until $ab$ itself is chosen;
terminal maximality forces it to be chosen eventually.  Distinct fan targets
all lie in $\U_n$, so they are mutually incomparable unless they are equal, and
the graph edges are distinct.  Thus the captured edges account for $C$ distinct
eventual game moves (one of which, $a_0b$, is Prolonger's own capture play),
while the individually deleted edges counted by $X$ are themselves distinct
game moves realized by Shortener's exact-target choices.  Hence
\[
  \L(n)\ge C+X
  \ge
  \frac{|E_0|}{2}
  \ge
  \left(\frac18-o_\delta(1)\right)
  \frac{n\log\log n}{\log n},
\]
by \eqref{eq:surviving-fan-count} and \eqref{eq:fan-capture-half}.  Since
$\delta$ was fixed, this proves the theorem.
\end{proof}

\subsection{The conditional T2 theorem}

The preceding fan-capture theorem gives an unconditional game lower bound.
A different, potentially larger lower-bound mechanism uses residual upper-half
targets of the form $acb$, where $a,c$ are small primes and $b$ lies in a
corresponding large-prime interval.  The resulting residual game is modeled by
a scored rank-three slot hypergraph.

The finite potential argument which one would like to use in this slot
hypergraph is not true for arbitrary finite capture games.  The counterexample
in \Cref{prop:t2-max-gain-counterexample} shows that a unique max-gain Maker
move need not dominate every subsequent Breaker deletion, and
\Cref{prop:t2-safe-edge-refutation} shows that the general safe-edge property
already fails inside the residual arithmetic games.  We therefore state the
lower bound conditionally on a restricted property for the states generated by
the specific activation and residual strategies.

\begin{definition}[Restricted safe-edge hypothesis]\label{def:safe-edge}
In each finite graph or scored rank-three hypergraph state actually reached by
the T2 activation strategy and subsequent residual slot construction, assume
that whenever a positive-weight live edge exists, Maker has a legal live edge
$f$ such that, after Maker plays $f$, every legal Breaker reply leaves the
scaled potential $Q$, as defined in the finite slot-game setup of
\Cref{app:deferred-proofs}, at least as large as it was before Maker's move.
\end{definition}

\begin{theorem}[Conditional T2 lower bound]\label{thm:t2}
Assume the restricted safe-edge hypothesis for the finite graph and residual
slot-hypergraph states generated by the construction in
\Cref{app:deferred-proofs}.  Then for every fixed $0<\delta<1/4$ there is a
constant $c_\delta>0$ such that
\[
  \L(n)\ge c_\delta\,\frac{n(\log\log n)^2}{\log n}
\]
for all sufficiently large $n$.
\end{theorem}

\begin{proof}
See \Cref{prop:t2-final} in \Cref{app:deferred-proofs}.  The full proof
assembles \Cref{prop:t2-activation-potential,prop:t2-deletion-budget,%
prop:t2-residual-mass,prop:t2-residual-embedding} under the restricted
safe-edge hypothesis of \Cref{def:safe-edge}.
\end{proof}
