
\section{The Main Upper Bound}\label{sec:main-upper}

In this section we prove the paper's headline upper bound
\[
  \L(n) \le \left(\frac{\Wfour}{2}+o(1)\right)n < 0.19n.
\]
The proof uses the following explicit strategy.  Shortener plays the smallest legal odd prime for a long initial prefix of
\[
  K = \left\lfloor \frac{(1-\eps)n}{2\log n}\right\rfloor
\]
turns.  This prefix is available for all sufficiently large $n$.

\begin{lemma}[Existence of the odd-prime prefix]\label{lem:prefix-existence}
Fix $0<\eps<1$ and
\[
  K=\left\lfloor \frac{(1-\eps)n}{2\log n}\right\rfloor.
\]
For all sufficiently large $n$, before each of Shortener's first $K$ turns
there is a legal odd prime.  Hence the smallest-legal-odd-prime strategy can
be followed for a prefix of $K$ Shortener moves.
\end{lemma}

\begin{proof}
Consider the moment before Shortener's $j$th move in this prefix, with
$1\le j\le K$.  At most $2j-1$ previous moves have occurred.  A previous move
$x\le n$ can make at most one odd prime $p>\sqrt n$ illegal: if two such
primes divided $x$, then $x>n$, while the only other way for $x$ to be
comparable with such a prime is $x=p$ itself.  Thus at most $2j-1$ odd primes
in $(\sqrt n,n]$ have been made illegal.

By the prime number theorem,
\[
  \pi(n)-\pi(\sqrt n)\sim \frac{n}{\log n}>2K
\]
for all sufficiently large $n$.  Since $2j-1<2K$, at least one odd prime
$p\in(\sqrt n,n]$ remains legal before Shortener's $j$th prefix move.  In
particular the game has not ended, and Shortener's rule has a legal odd prime
to play.
\end{proof}

Let
\[
  q_1 < q_2 < \cdots < q_K
\]
be the odd primes she plays during that prefix.  The argument has four layers:
\begin{enumerate}
  \item a local density law for the counting function of the $q_j$;
  \item a monotone envelope and inversion producing a comparison sequence
    $b_j \ge q_j$ with explicit moment limits;
  \item a fourth-order Bonferroni comparison theorem for arbitrary increasing
    odd-prime comparison sequences;
  \item a prime-rounding bridge that replaces the real sequence $b_j$ by actual
    odd primes $p_j$, using the key half-density slack supplied by the
    prime-rounding bridge of \Cref{thm:prime-bridge}.
\end{enumerate}

\subsection{The local density}

Write
\[
  S_K(X) := \#\{j\le K : q_j \le X\},
  \qquad
  u := \frac{\log X}{\log n}.
\]
On the interval
\[
  u \in \left(\frac{1}{h+1},\frac1h\right],
\]
the local prime-counting law identifies the limiting captured-prime density as
\[
  \rhoU(u) = \frac{1}{(\lfloor 1/u \rfloor+1)u} = \frac{1}{(h+1)u}.
\]

\begin{lemma}[Local prime-count per range]\label{lem:prime-count-per-range}
Let Shortener follow the smallest-legal-odd-prime strategy.  Fix an integer
$h\ge1$ and real numbers $2\le Y<X\le n$ with
\[
  Y^{h+1}>n.
\]
Let $S(X)$ be the number of odd primes at most $X$ which Shortener has played
by the first time her next odd-prime move would exceed $X$ (or by terminal time,
if no such move occurs).  Then
\[
  S(X)\ge\frac{\pi(X)-\pi(Y)}{h+1}-O_h(1).
\]
In particular, if $n^{1/(h+1)}<Y<X\le n^{1/h}$, then every prime
$p\in(Y,X]$ lies in the packet regime $p^h\le n<p^{h+1}$ and the same lower
bound holds.
\end{lemma}

\begin{proof}
Shortener's odd-prime moves are increasing: once a prime has become illegal it
cannot become legal later, and the strategy always chooses the smallest legal
odd prime.  At the stopping time in the definition of $S(X)$, no odd prime
$p\le X$ is still legal.  Therefore every odd prime $p\in(Y,X]$ has one of two
forms: either Shortener herself has played $p$, or some earlier Prolonger move
was divisible by $p$.

Let
\[
  M:=\#\{p\in\PP:\ Y<p\le X,\ p\text{ odd}\}.
\]
The number of primes counted by $M$ that Shortener has played is at most
$S(X)$.  There are at most $S(X)+1$ Prolonger moves before the stopping time.
Each such move is an integer at most $n$, so it is divisible by at most $h$
distinct primes from $(Y,X]$: otherwise it would be at least
$Y^{h+1}>n$.  Hence
\[
  M\le S(X)+h(S(X)+1)=(h+1)S(X)+h.
\]
Thus
\[
  S(X)\ge \frac{M-h}{h+1}.
\]
Finally $M=\pi(X)-\pi(Y)+O(1)$, the $O(1)$ accounting only for the prime $2$
and endpoint conventions.  This gives the claimed bound.  If
$n^{1/(h+1)}<Y<X\le n^{1/h}$ and $p\in(Y,X]$, then $p^h\le X^h\le n$ while
$p^{h+1}>Y^{h+1}>n$, so this is exactly the stated packet regime.
\end{proof}

\begin{proposition}[Local density away from breakpoints]\label{prop:local-density}
Fix $H\ge 2$, and set
\[
  \tau_H := \frac{1}{8H^2}.
\]
For $1\le h\le H-1$, define
\[
  \alpha_h := \frac{1}{h+1}+\tau_H,
  \qquad
  \beta_h := \frac1h-\tau_H,
  \qquad
  I_h := [\alpha_h,\beta_h].
\]
Then there exists a function $\xi_H(n)\to 0$ such that, for all sufficiently
large $n$, for every $1\le h\le H-1$ and every $u\in I_h$,
\[
  S_K(n^u)
  \ge
  \bigl(1-\xi_H(n)\bigr)\frac{n^u}{(h+1)u\log n}.
\]
\end{proposition}

\begin{proof}
The intervals $I_h$ are nonempty, because
\[
  \beta_h-\alpha_h
  =
  \frac1h-\frac1{h+1}-2\tau_H
  \ge
  \frac{1}{H(H-1)}-\frac{1}{4H^2}
  >
  0.
\]
Fix $1\le h\le H-1$ and $u\in I_h$, and put
\[
  \eta := \frac{\tau_H}{2},
  \qquad
  X := n^u,
  \qquad
  Y := n^{u-\eta}.
\]
Since $u\in I_h$,
\[
  u-\eta \ge \frac{1}{h+1}+\frac{\tau_H}{2} > \frac{1}{h+1},
  \qquad
  u \le \frac1h-\tau_H < \frac1h.
\]
Hence the entire interval $[u-\eta,u]$ stays inside
$\bigl(\frac{1}{h+1},\frac1h\bigr)$.  Thus $Y^{h+1}>n$, and
\Cref{lem:prime-count-per-range} yields
\[
  S(X)
  \ge
  \frac{\pi(X)-\pi(Y)}{h+1}-O_H(1),
\]
where $S(X)$ denotes the number of odd primes played by Shortener up to the
first time her move exceeds $X$.

Assuming the prime prefix exists for all $K$ Shortener moves, as guaranteed
for large $n$ by \Cref{lem:prefix-existence}, we claim that $S(X)=S_K(X)$ for
all $u\in\bigcup_{h=1}^{H-1}I_h$ once $n$ is large enough.  Indeed,
$u\le \beta_1=1-\tau_H$, so by the prime number theorem,
\[
  \pi(n^u)
  \ll \frac{n^{1-\tau_H}}{\log n}
  =
  o\!\left(\frac{n}{\log n}\right)
  =
  o(K).
\]
Therefore all odd primes at most $X=n^u$ are exhausted before the prefix of
length $K$, and the local counting function $S(X)$ coincides with the truncated
counting function $S_K(X)$.

Substituting $X=n^u$ and $Y=n^{u-\eta}$ gives
\[
  S_K(n^u)
  \ge
  \frac{\pi(n^u)-\pi(n^{u-\eta})}{h+1}-O_H(1).
\]
Now $u$ ranges over the fixed compact interval $I_h$, so the prime number
theorem is uniform there:
\[
  \pi(n^u)=\bigl(1+o_H(1)\bigr)\frac{n^u}{u\log n}.
\]
Also $u-\eta\le u-\tau_H/2$, hence
\[
  \frac{\pi(n^{u-\eta})}{n^u/(u\log n)}
  \ll_H
  u\,n^{-\eta}
  =
  o_H(1)
\]
uniformly for $u\in I_h$.  Since there are only finitely many blocks
$1\le h\le H-1$, we may absorb the error terms into a single function
$\xi_H(n)\to 0$, valid simultaneously for every $h$ and every $u\in I_h$.
This gives
\[
  S_K(n^u)
  \ge
  \bigl(1-\xi_H(n)\bigr)\frac{n^u}{(h+1)u\log n},
\]
as claimed.
\end{proof}

\subsection{Moment constants and the Bonferroni coefficient}

Define
\[
  J_r
  :=
  \frac1{r!}
  \int_{\substack{u_1+\cdots+u_r\le 1\\u_i\in(0,1]}}
  \prod_{i=1}^r \rhoU(u_i)\,du_1\cdots du_r,
\]
and
\[
  \Wfour := 1-J_1+J_2-J_3+J_4.
\]
The interval-arithmetic certification in \Cref{prop:wfour-certification} gives
\[
  \frac{\Wfour}{2}\le 0.1897123371<0.19.
\]

For any increasing sequence $b_1\le \cdots \le b_K$ of positive reals, define
the truncated factorial-moment sums
\[
  T_r^{(b)}(n)
  :=
  \sum_{\substack{1\le j_1<\cdots<j_r\le K\\b_{j_1}\cdots b_{j_r}\le n}}
  \frac{1}{b_{j_1}\cdots b_{j_r}}
  \qquad (1\le r\le 4).
\]

\subsection{Monotone envelope and inversion}

The local density from \Cref{prop:local-density} is piecewise-defined, so one
must build a monotone global comparison sequence before applying the
Bonferroni comparison.

\begin{proposition}[Envelope and inversion]\label{prop:envelope-inversion}
Fix $H\ge 2$, and define $\tau_H,\alpha_h,\beta_h,I_h$ as in
\Cref{prop:local-density}.  Put
\[
  G_H := \bigcup_{h=1}^{H-1} I_h,
\]
and for $1\le r\le 4$ define
\[
  J_r^{(H)}
  :=
  \frac1{r!}
  \int_{\substack{u_1+\cdots+u_r\le 1\\u_i\in G_H}}
  \prod_{i=1}^r \rhoU(u_i)\,du_1\cdots du_r.
\]
Then for every sufficiently large $n$ there exists a monotone function
$C_{H,n}:[2,n]\to\{0,1,\dots,K\}$ such that:
\begin{enumerate}
  \item $C_{H,n}(X)\le S_K(X)$ for all $2\le X\le n$;
  \item if
    \[
      b_j := \inf\{X\in[2,n]: C_{H,n}(X)\ge j\},
    \]
    then $q_j \le b_j$ for every $1\le j\le K$;
  \item for every fixed $r\in\{1,2,3,4\}$,
    \[
      T_r^{(b)}(n)=J_r^{(H)}+o_H(1)
      \qquad (n\to\infty);
    \]
  \item for every fixed $r\in\{1,2,3,4\}$,
    \[
      0\le J_r-J_r^{(H)}\le \frac{5r}{4H\,r!}.
    \]
\end{enumerate}
In particular, there exists an integer-valued function $H_*(n)\to\infty$ and a
corresponding choice of comparison sequences
\[
  b_1^{(n)}\le \cdots \le b_K^{(n)}
\]
obtained from the above construction with $H=H_*(n)$ such that
\[
  T_r^{(b^{(n)})}(n)=J_r+o(1)
  \qquad (1\le r\le 4).
\]
\end{proposition}

\begin{proof}
By \Cref{prop:local-density}, there is a function $\xi_H(n)\to 0$ such that
for every large enough $n$, every $1\le h\le H-1$, and every $u\in I_h$,
\[
  S_K(n^u)
  \ge
  \bigl(1-\xi_H(n)\bigr)\frac{n^u}{(h+1)u\log n}.
\]
Define
\[
  A_{n,h}(u)
  :=
  \bigl(1-\xi_H(n)\bigr)\frac{n^u}{(h+1)u\log n}
  \qquad (u\in I_h).
\]
For fixed $H$ and all sufficiently large $n$, the functions $A_{n,h}$ are
strictly increasing on $I_h$, since
\[
  A_{n,h}'(u)
  =
  \bigl(1-\xi_H(n)\bigr)\frac{n^u}{(h+1)u}
  \left(1-\frac{1}{u\log n}\right),
\]
and $u\ge \alpha_{H-1}>1/H$.

Set
\[
  L_h := \lfloor A_{n,h}(\alpha_h)\rfloor,
  \qquad
  R_h := \lfloor A_{n,h}(\beta_h)\rfloor
  \qquad (1\le h\le H-1).
\]
Then $L_h\le R_h$.  Moreover, for $2\le h\le H-1$,
\[
  \frac{A_{n,h-1}(\alpha_{h-1})}{A_{n,h}(\beta_h)}
  =
  n^{2\tau_H}\cdot
  \frac{(h+1)(1/h-\tau_H)}{h(1/h+\tau_H)}
  \to \infty,
\]
so $R_h\le L_{h-1}$ for all large $n$.  Also
\[
  R_1 \ll \frac{n^{1-\tau_H}}{\log n}=o(K),
\]
again for large $n$.  Thus, after increasing $n$ if necessary,
\[
  0\le L_{H-1}\le R_{H-1}\le L_{H-2}\le R_{H-2}\le \cdots \le L_1\le R_1<K.
\]

We now define the cumulative lower envelope by
\[
  C_{H,n}(X):=
  \begin{cases}
    0, & 2\le X<n^{\alpha_{H-1}},\\[1mm]
    \lfloor A_{n,h}(\log_n X)\rfloor,
      & n^{\alpha_h}\le X\le n^{\beta_h}\quad (1\le h\le H-1),\\[1mm]
    R_h, & n^{\beta_h}<X<n^{\alpha_{h-1}}\quad (2\le h\le H-1),\\[1mm]
    R_1, & n^{\beta_1}<X<n,\\[1mm]
    K, & X=n.
  \end{cases}
\]
This function is monotone nondecreasing: it is nondecreasing on each genuine
block because $A_{n,h}$ is increasing, it is constant on each gap, and the
relations $R_h\le L_{h-1}$ guarantee monotonicity across adjacent pieces.

We next prove that $C_{H,n}(X)\le S_K(X)$ for all $2\le X\le n$.  If
$X\in[n^{\alpha_h},n^{\beta_h}]$, then
\[
  C_{H,n}(X)
  =
  \lfloor A_{n,h}(\log_n X)\rfloor
  \le
  S_K(X)
  \qquad
  \text{by the definition of $A_{n,h}$}.
\]
If $X\in(n^{\beta_h},n^{\alpha_{h-1}})$ with $2\le h\le H-1$, then
\[
  C_{H,n}(X)=R_h\le S_K(n^{\beta_h})\le S_K(X),
\]
since $S_K$ is nondecreasing.  The same argument gives
$C_{H,n}(X)=R_1\le S_K(X)$ on $(n^{\beta_1},n)$, while
$C_{H,n}(X)=0\le S_K(X)$ below $n^{\alpha_{H-1}}$ and
$C_{H,n}(n)=K=S_K(n)$.  This proves part~(1).

Define
\[
  b_j := \inf\{X\in[2,n]: C_{H,n}(X)\ge j\}
  \qquad (1\le j\le K).
\]
Because $C_{H,n}$ is nondecreasing, the sequence $(b_j)_{j=1}^K$ is
nondecreasing.  Moreover,
\[
  S_K(b_j)\ge C_{H,n}(b_j)\ge j,
\]
so the $j$th prime in the prime prefix satisfies $q_j\le b_j$.  This proves
part~(2).

For the moment asymptotics, write
\[
  u_j := \log_n b_j,
  \qquad
  w_j := \frac{1}{b_j}=n^{-u_j},
  \qquad
  \mu_{H,n} := \sum_{j=1}^K w_j\,\delta_{u_j}.
\]
Split $\mu_{H,n}=\nu_{H,n}+\lambda_{H,n}$, where $\nu_{H,n}$ is the
contribution from the genuine interval blocks
$L_h<j\le R_h$, and $\lambda_{H,n}$ is the contribution from the flat filler
blocks.

The filler blocks have negligible reciprocal mass.  For the bottom block,
\[
  |\lambda_{H,n}^{\mathrm{bot}}|
  =
  L_{H-1}n^{-\alpha_{H-1}}
  \le
  A_{n,H-1}(\alpha_{H-1})n^{-\alpha_{H-1}}
  =
  \frac{1-\xi_H(n)}{H\alpha_{H-1}\log n}
  =
  O_H\!\left(\frac1{\log n}\right).
\]
For a gap block between $I_h$ and $I_{h-1}$, where $2\le h\le H-1$,
\[
  |\lambda_{H,n}^{(h)}|
  =
  (L_{h-1}-R_h)n^{-\alpha_{h-1}}
  \le
  L_{h-1}n^{-\alpha_{h-1}}
  \le
  \frac{1-\xi_H(n)}{h\,\alpha_{h-1}\log n}
  =
  O_H\!\left(\frac1{\log n}\right).
\]
For the top block,
\[
  |\lambda_{H,n}^{\mathrm{top}}|
  =
  (K-R_1)n^{-1}
  \le
  \frac{K}{n}
  =
  O\!\left(\frac1{\log n}\right).
\]
Since there are only $O_H(1)$ filler blocks,
\[
  |\lambda_{H,n}|
  =
  O_H\!\left(\frac1{\log n}\right)
  =
  o_H(1).
\]

We next analyze the genuine blocks.  Fix $1\le h\le H-1$.  On the block
$L_h<j\le R_h$, the value $u_j=:u_{h,j}\in I_h$ is defined by
$A_{n,h}(u_{h,j})=j$.  Therefore, for every $f\in C^1([0,1])$,
\[
  \int f\,d\nu_{H,n}^{(h)}
  =
  \sum_{j=L_h+1}^{R_h} f(u_{h,j})n^{-u_{h,j}}
  =
  \int_{\alpha_h}^{\beta_h} f(u)n^{-u}\,d\lfloor A_{n,h}(u)\rfloor.
\]
Let
\[
  R_{n,h}(u):=\lfloor A_{n,h}(u)\rfloor-A_{n,h}(u),
  \qquad |R_{n,h}(u)|\le 1.
\]
Applying Stieltjes integration by parts with
$g(u):=f(u)n^{-u}$ gives
\[
  \int_{\alpha_h}^{\beta_h} g(u)\,d\lfloor A_{n,h}(u)\rfloor
  =
  \int_{\alpha_h}^{\beta_h} g(u)\,dA_{n,h}(u)
  +
  E_{n,h}(f),
\]
where
\[
  |E_{n,h}(f)|
  \le
  2\|g\|_\infty+\int_{\alpha_h}^{\beta_h}|g'(u)|\,du.
\]
Since
\[
  g'(u)=\bigl(f'(u)-(\log n)f(u)\bigr)n^{-u},
\]
we obtain
\[
  |E_{n,h}(f)|
  \le
  2\|f\|_\infty n^{-\alpha_h}
  +(\beta_h-\alpha_h)\|f'\|_\infty n^{-\alpha_h}
  +(\beta_h-\alpha_h)(\log n)\|f\|_\infty n^{-\alpha_h}
  =
  o_H(1).
\]
On the other hand,
\[
  n^{-u}A_{n,h}'(u)
  =
  \bigl(1-\xi_H(n)\bigr)\rhoU(u)
  \left(1-\frac{1}{u\log n}\right)
  \qquad (u\in I_h),
\]
because $\rhoU(u)=1/((h+1)u)$ on $I_h$.  Hence
\[
  \int_{\alpha_h}^{\beta_h} f(u)n^{-u}\,dA_{n,h}(u)
  =
  \bigl(1-\xi_H(n)\bigr)\int_{\alpha_h}^{\beta_h}
  f(u)\rhoU(u)\left(1-\frac{1}{u\log n}\right)\,du
  =
  \int_{I_h} f(u)\rhoU(u)\,du+o_H(1),
\]
uniformly for fixed $f$.  Combining the last two displays yields
\[
  \int f\,d\nu_{H,n}^{(h)}
  =
  \int_{I_h} f(u)\rhoU(u)\,du+o_H(1).
\]
Summing over $h$ and using $|\lambda_{H,n}|=o_H(1)$, we find that for every
$f\in C^1([0,1])$,
\[
  \int f\,d\mu_{H,n}
  =
  \int_{G_H} f(u)\rhoU(u)\,du+o_H(1).
\]
Taking $f\equiv1$ gives $\mu_{H,n}([0,1])=O_H(1)$.

Fix $r\in\{1,2,3,4\}$, and write
\[
  \Sigma_r:=\{(u_1,\dots,u_r)\in[0,1]^r:u_1+\cdots+u_r\le 1\}.
\]
Then
\[
  \int_{\Sigma_r} d\mu_{H,n}^{\otimes r}
  =
  \sum_{j_1,\dots,j_r}
  \mathbf 1_{\{u_{j_1}+\cdots+u_{j_r}\le 1\}}
  \prod_{t=1}^r w_{j_t}.
\]
The contribution of distinct ordered $r$-tuples is exactly
$r!\,T_r^{(b)}(n)$, because
$u_{j_1}+\cdots+u_{j_r}\le 1$ is equivalent to
$b_{j_1}\cdots b_{j_r}\le n$.  The repeated-index contribution is negligible:
\[
  \max_j w_j \le n^{-\alpha_{H-1}} \to 0,
\]
while $\mu_{H,n}([0,1])=O_H(1)$ by the preceding $f\equiv1$ bound.
Therefore
\[
  0
  \le
  \int_{\Sigma_r} d\mu_{H,n}^{\otimes r}-r!\,T_r^{(b)}(n)
  \le
  \binom{r}{2}\bigl(\max_j w_j\bigr)\mu_{H,n}([0,1])^{r-1}
  =
  o_H(1).
\]
The same Riemann-sum convergence tensorizes: for every continuous
$F$ on $[0,1]^r$,
\[
  \int F\,d\mu_{H,n}^{\otimes r}
  \to
  \int_{G_H^r}F(u_1,\ldots,u_r)
  \prod_{i=1}^r\rhoU(u_i)\,du_1\cdots du_r.
\]
The indicator of $\Sigma_r$ restricted to $G_H^r$ is Riemann integrable,
because its discontinuities lie on the finitely many coordinate breakpoints
and on the hyperplane $u_1+\cdots+u_r=1$.  Approximating this indicator from
above and below by continuous functions therefore gives
\[
  \int_{\Sigma_r} d\mu_{H,n}^{\otimes r}
  \to
  \int_{\substack{u_1+\cdots+u_r\le 1\\u_i\in G_H}}
  \prod_{i=1}^r \rhoU(u_i)\,du_1\cdots du_r
  =
  r!\,J_r^{(H)}.
\]
Combining the last two displays proves part~(3):
\[
  T_r^{(b)}(n)=J_r^{(H)}+o_H(1).
\]

It remains to control the excised breakpoint region.  Since
$0<\rhoU(u)<1$ on $(0,1]$, we have
\[
  0\le J_r-J_r^{(H)}
  \le
  \frac1{r!}\,
  \lambda_r\bigl(\{(u_1,\dots,u_r)\in[0,1]^r:\exists i,\ u_i\notin G_H\}\bigr),
\]
where $\lambda_r$ denotes $r$-dimensional Lebesgue measure.  Moreover,
\[
  |(0,1]\setminus G_H|
  =
  \frac1H+2(H-1)\tau_H
  \le
  \frac1H+\frac{1}{4H}
  =
  \frac{5}{4H}.
\]
By the union bound in $[0,1]^r$,
\[
  \lambda_r\bigl(\{(u_1,\dots,u_r)\in[0,1]^r:\exists i,\ u_i\notin G_H\}\bigr)
  \le
  r\,|(0,1]\setminus G_H|
  \le
  \frac{5r}{4H}.
\]
This proves part~(4), and the final statement follows immediately by first
letting $n\to\infty$ for fixed $H$, and then letting $H\to\infty$.

To obtain a single comparison sequence for each $n$, choose $N_H$ so large
that for all $n\ge N_H$ the above construction is valid and, for every
$1\le r\le 4$,
\[
  \bigl|T_r^{(b)}(n)-J_r^{(H)}\bigr|\le \frac1H.
\]
After enlarging if necessary, we may assume $N_H$ is increasing in $H$.  Define
\[
  H_*(n):=\max\{H\ge 2:N_H\le n\},
\]
and let $b_1^{(n)}\le\cdots\le b_K^{(n)}$ be the comparison sequence produced
with parameter $H=H_*(n)$.  Then $H_*(n)\to\infty$, and for every
$1\le r\le 4$,
\[
  \bigl|T_r^{(b^{(n)})}(n)-J_r\bigr|
  \le
  \bigl|T_r^{(b^{(n)})}(n)-J_r^{(H_*(n))}\bigr|
  +
  \bigl|J_r^{(H_*(n))}-J_r\bigr|
  \le
  \frac{1}{H_*(n)}+\frac{5r}{4H_*(n)r!},
\]
which tends to $0$.  This proves the final statement.
\qedhere
\end{proof}

\subsection{The prime-sequence Bonferroni comparison theorem}

The comparison theorem must be stated for \emph{prime sequences}, not for
arbitrary reals; the correct statement is the following.

\begin{lemma}[Odd-sieve monotonicity under prime upgrades]
\label{lem:odd-sieve-monotonicity}
Let $q_1<\cdots<q_K$ and $p_1<\cdots<p_K$ be odd primes with
$q_j\le p_j$ for every $j$.  If $N(r_1,\ldots,r_K)$ denotes the number of odd
integers $m\le n$ not divisible by any of the primes $r_1,\ldots,r_K$, then
\[
  N(q_1,\ldots,q_K)\le N(p_1,\ldots,p_K).
\]
\end{lemma}

\begin{proof}
Replace the primes one at a time, in descending order of the index.  Suppose
the primes other than the $k$th one form a set $R$, and let $q\le p$ be the
two possible $k$th primes, neither lying in $R$.  Let $A_R(t)$ be the number
of odd integers at most $t$ which are divisible by no prime in $R$.  Since $q$
and $p$ are distinct from every prime in $R$,
\[
  N(R\cup\{q\})=A_R(n)-A_R(n/q),
  \qquad
  N(R\cup\{p\})=A_R(n)-A_R(n/p).
\]
The function $A_R(t)$ is nondecreasing, and $q\le p$, so
$A_R(n/q)\ge A_R(n/p)$.  Hence replacing $q$ by $p$ can only increase the
survivor count.  Descending replacement preserves distinctness and the sorted
structure, because after the indices $>k$ have been upgraded we still have
$q_{k-1}<q_k\le p_k<p_{k+1}$, with the obvious endpoint omissions.
\end{proof}

\begin{theorem}[Prime-sequence Bonferroni--4 comparison]\label{thm:bonf-comp}
Let $q_1<\cdots<q_K$ be the actual odd primes played by Shortener during the
prime prefix, and let $p_1<\cdots<p_K$ be any increasing sequence of odd
primes with
\[
  q_j \le p_j \qquad (1\le j\le K).
\]
Assume that for $1\le r\le 4$,
\[
  T_r^{(p)}(n) = \Lambda_r + o(1).
\]
Then
\[
  \L(n)
  \le
  \frac n2\left(1-\Lambda_1+\Lambda_2-\Lambda_3+\Lambda_4+o(1)\right).
\]
\end{theorem}

\begin{proof}
Let $A$ be the final played set.  If the game ends before Shortener completes
the prefix of length $K$, then $\L(n)=o(n)$ and there is nothing to prove, so
assume $q_1,\dots,q_K$ were all played.

Define the odd-part map
\[
  \varphi(x) := \frac{x}{2^{v_2(x)}}.
\]
If $\varphi(x)=\varphi(y)=m$, then $x=2^a m$ and $y=2^b m$.  If $a\neq b$, one
of $x$ and $y$ divides the other, contradicting that $A$ is an antichain.  So
$\varphi$ is injective on $A$.

Since each $q_j\in A$, no other element of $A$ can be divisible by any $q_j$.
Because $q_j$ is odd, divisibility by $q_j$ is preserved under the odd-part
map.  Hence
\[
  \varphi(A)
  \subseteq
  \{m\le n : m \text{ odd and } q_j\nmid m \text{ for all } j\}
  \cup \{q_1,\dots,q_K\}.
\]
Therefore
\[
  \L(n) \le N(q_1,\dots,q_K) + K = N(q_1,\dots,q_K)+o(n),
\]
where $N(q_1,\dots,q_K)$ counts odd integers up to $n$ avoiding all $q_j$.

Now replace the actual sequence $q_j$ by the larger prime sequence $p_j$.
\Cref{lem:odd-sieve-monotonicity} gives
\[
  N(q_1,\dots,q_K) \le N(p_1,\dots,p_K).
\]
Applying fourth-order Bonferroni to the divisibility events $p_j \mid m$ over
odd integers $m\le n$ gives
\[
\begin{aligned}
  N(p_1,\dots,p_K)
  \le\;&
  \frac n2
  \left(1-T_1^{(p)}(n)+T_2^{(p)}(n)-T_3^{(p)}(n)+T_4^{(p)}(n)\right) \\
  &\quad + O(D_1+D_2+D_3+D_4),
\end{aligned}
\]
where
\[
  D_r:=
  \#\{j_1<\cdots<j_r:p_{j_1}\cdots p_{j_r}\le n\}.
\]
Indeed, for a fixed $r$-tuple $J=\{j_1<\cdots<j_r\}$ with
$P_J:=\prod_{j\in J}p_j\le n$, the number of odd $m\le n$ divisible by
$P_J$ is
\[
  \frac{n}{2P_J}+O(1),
\]
because $P_J$ is odd.  If $P_J>n$ the intersection is empty, so the total
floor error in the first four Bonferroni sums is
$O(D_1+D_2+D_3+D_4)$.

We use the standard Landau bound for squarefree integers with exactly $r$
prime factors (see, for example, \cite[Ch.~22]{HardyWright08}),
\[
  \#\{m\le n:m\text{ squarefree and }\omega(m)=r\}
  =
  O_r\!\left(\frac{n(\log\log n)^{r-1}}{\log n}\right).
\]
Every product counted by $D_r$ is such a squarefree integer, and therefore
\[
  D_r
  =
  O_r\!\left(\frac{n(\log\log n)^{r-1}}{\log n}\right)
  =
  o(n)
  \qquad (1\le r\le4),
\]
so the error is $o(n)$.  Substituting $T_r^{(p)}(n)=\Lambda_r+o(1)$ yields the
stated inequality.
\end{proof}

\subsection{The prime-rounding bridge}

\begin{lemma}[Fixed-ratio cell reciprocal mass]\label{lem:cell-reciprocal-mass}
Fix $H\ge2$, and let $b_1,\ldots,b_K$ be the comparison sequence obtained from
\Cref{prop:envelope-inversion} with this fixed $H$.  For every fixed $c>1$,
uniformly in $Y>0$,
\[
  \sum_{\substack{1\le j\le K\\Y\le b_j<cY}}\frac1{b_j}
  =
  O_{H,c}\!\left(\frac1{\log n}\right).
\]
\end{lemma}

\begin{proof}
If the cell $[Y,cY)$ lies inside a genuine block
$[n^{\alpha_h},n^{\beta_h}]$, then $B_{H,n}(X):=\#\{j:b_j\le X\}$ agrees with
$\lfloor A_{n,h}(\log_n X)\rfloor$ on the block.  As in the proof of
\Cref{prop:envelope-inversion},
\[
  \frac{d}{dX}A_{n,h}(\log_n X)
  =
  \frac{1-\xi_H(n)}{(h+1)\log X}
  \left(1-\frac1{\log X}\right)
  \ll_H \frac1{\log n},
\]
because every genuine block has $X\ge n^{\alpha_{H-1}}>n^{1/H}$.  Hence
\[
  \#\{j:Y\le b_j<cY,\ j\text{ genuine}\}
  \ll_{H,c}\frac{Y}{\log n}+1.
\]
Dividing by $Y$ gives a reciprocal contribution $O_{H,c}(1/\log n)$; the
endpoint $+1$ is harmless since $Y\ge n^{1/H}$ in a genuine block.

A fixed-ratio cell can meet at most one breakpoint for all large $n$, because
successive breakpoints in the envelope are separated by a factor which is a
positive power of $n$.  If the cell is adjacent to a breakpoint, split its
genuine part into the at most two adjacent genuine pieces and apply the
preceding estimate to each.  The only additional contribution is the flat atom
at the breakpoint.  At $A_h:=n^{\alpha_h}$ the flat multiplicity is at most
$L_h$, so
\[
  \frac{L_h}{A_h}
  \le
  \frac{A_{n,h}(\alpha_h)}{n^{\alpha_h}}
  =
  O_H\!\left(\frac1{\log n}\right).
\]
The top flat block at $b_j=n$ contributes at most
\[
  \frac{K}{n}=O\!\left(\frac1{\log n}\right).
\]
Cells lying wholly in gaps have no genuine contribution and only the same
possible flat-atom contribution.  These cases cover all $Y$.
\end{proof}

It remains to convert the real comparison sequence $b_j$ from
\Cref{prop:envelope-inversion} into an actual increasing odd-prime sequence.
The naive claim
\[
  p_j/b_j = 1 + O(1/\log b_j)
\]
uniformly in $j$ is \emph{not} justified by the prime number theorem alone and
must not be used.  The correct bridge is the half-density construction of
\Cref{thm:prime-bridge}.

\begin{proposition}[Fixed-parameter queued prime rounding]
\label{prop:queued-prime-rounding}
Fix $H\ge2$ and $\lambda>1$, and choose $a>1$ with $a^2\le\lambda$.
Let $b_1,\ldots,b_K$ be the comparison sequence obtained from
\Cref{prop:envelope-inversion} with this fixed $H$.  Then there is an
increasing sequence of odd primes $p_1<\cdots<p_K$ such that
\[
  q_j\le b_j\le p_j\qquad (1\le j\le K),
\]
and, for every fixed $1\le r\le4$,
\[
  T_r^{(p)}(n)=T_r^{(b)}(n)+O_{H,r}(\lambda-1)+o_{H,\lambda}(1).
  \tag{7.1}\label{eq:queued-bridge-moment}
\]
\end{proposition}

\begin{proof}
Write
\[
  A_h:=n^{\alpha_h},\qquad B_h:=n^{\beta_h}\qquad (1\le h\le H-1).
\]
Fix one genuine block $[A_h,B_h]$ and abbreviate $A=A_h$, $B=B_h$.  Partition
it into fixed multiplicative bins
\[
  I_k=[Aa^k,Aa^{k+1})\qquad (k=0,1,\ldots,M),
\]
where the last bin is truncated at $B$.  Let
\[
  d_k:=\#\{j:b_j\in I_k,\ j\text{ lies in the genuine }h\text{-block}\}
\]
and let $f_h$ be the multiplicity of the flat atom at the left endpoint
$A_h$.  Thus $f_{H-1}$ is the bottom flat atom, and for $h<H-1$ it is the flat
atom in the gap just below $A_h$.

We first record the fixed-ratio estimates used by the queue.  For every fixed
$c>1$, uniformly for $X\ge n^{1/H}$ with $[X,cX]\subseteq[A_h,B_h]$,
\[
  \#\{j:X\le b_j<cX,\ j\text{ genuine in block }h\}
  \le
  (1+o_{H,c}(1))\frac{(c-1)X}{(h+1)\log X}+O(1).
  \tag{7.2}\label{eq:genuine-bin-demand}
\]
Indeed, on a genuine block $B_{H,n}(Y)=\lfloor A_{n,h}(\log_nY)\rfloor$, and
\[
  \frac{d}{dY}A_{n,h}(\log_nY)
  =
  \frac{1-\xi_H(n)}{(h+1)\log Y}
  \left(1-\frac1{\log Y}\right).
\]
Integrating over $[X,cX]$ gives \eqref{eq:genuine-bin-demand}; the endpoint
error is negligible at the scales used below.  Similarly,
\[
  f_h\le (1+o_H(1))\frac{A_h}{(h+1)\log A_h},
  \tag{7.3}\label{eq:flat-atom-count}
\]
because $f_h\le L_h\le A_{n,h}(\alpha_h)$.  Finally, if
\[
  P_k:=\#\{p\text{ odd prime}:Aa^k\le p<Aa^{k+1}\},
\]
then the prime number theorem in fixed multiplicative intervals gives,
uniformly in $k$ in this fixed block,
\[
  P_k=(1+o_{H,a}(1))\frac{(a-1)Aa^k}{\log(Aa^k)}.
  \tag{7.4}\label{eq:prime-bin-count}
\]

Choose a small fixed $\eta>0$.  Since the demand has the factor
$1/(h+1)\le1/2$, we may choose an integer $s=s(a)$ such that
\[
  (1-\eta)(a^{s+1}-1)>(1+\eta)\frac{a^s}{2}.
  \tag{7.5}\label{eq:queue-clear}
\]
This is possible for every $a>1$.  For all large $n$, \eqref{eq:genuine-bin-demand},
\eqref{eq:flat-atom-count}, and the fact that $s$ is fixed give
\[
  f_h+\sum_{k=0}^{s-1}d_k
  \le
  (1+\eta)\frac{Aa^s}{2\log A},
\]
while \eqref{eq:prime-bin-count} gives
\[
  \sum_{\ell=0}^{s}P_\ell
  \ge
  (1-\eta)\frac{A(a^{s+1}-1)}{\log A}.
\]
By \eqref{eq:queue-clear}, the queue containing the flat atom and the first
$s$ genuine bins clears by the end of prime bin $s$.  More explicitly, the flat
atom is eligible for primes in bin $0$, and genuine demand from $I_k$ is
released only at prime bin $k+1$; processing prime bins in increasing order and
assigning available primes to the oldest unassigned demand therefore assigns
all these early demands to primes at least as large as their corresponding
$b_j$.

For each later full source bin $I_k$, $k\ge s$, assign its $d_k$ elements to
primes in the next prime bin $[Aa^{k+1},Aa^{k+2})$.  This is possible for all
large $n$, because \eqref{eq:genuine-bin-demand} and \eqref{eq:prime-bin-count} give
\[
  d_k
  \le
  (1+o_{H,a}(1))\frac{(a-1)Aa^k}{(h+1)\log(Aa^k)}
  <
  (1-o_{H,a}(1))\frac{(a-1)Aa^{k+1}}{\log(Aa^{k+1})}
  \le P_{k+1},
\]
using $1/(h+1)\le1/2<a$.  The final truncated source bin is handled in the
same way, using the next full prime bin above the block.

Call exceptional the flat atoms, the first $s(a)$ genuine bins of every genuine
block, and the top flat block $b_j=n$.  Let $E$ be the set of exceptional
indices.  By \Cref{lem:cell-reciprocal-mass}, each fixed multiplicative bin
has $b$-reciprocal mass $O_{H,a}(1/\log n)$, and there are only
$O_{H,a}(1)$ exceptional bins.  The top flat block contributes $K/n=O(1/\log n)$.
Thus
\[
  \sum_{j\in E}\frac1{b_j}=O_{H,a}\left(\frac1{\log n}\right).
  \tag{7.6}\label{eq:exceptional-b-mass}
\]
Since every assigned prime is at least the corresponding $b_j$, the same bound
holds with $p_j$ in place of $b_j$.

The top flat block is assigned, in order, to odd primes in $[n,2n]$.  This
interval contains $(1+o(1))n/\log n$ odd primes, more than enough for the at
most $K\le n/(2\log n)$ top flat indices.  Assignments from different genuine
blocks do not overlap.  The largest prime used for block $h$ is at most
$a^2B_h$, while the next larger block begins at
\[
  A_{h-1}=n^{1/h+\tau_H}=n^{2\tau_H}B_h,
\]
so $a^2B_h<A_{h-1}$ for large $n$.  Also $a^2B_1=o(n)$, so the top flat
assignment above $n$ comes last.  The construction therefore produces one
increasing prime sequence.  For every nonexceptional index,
\[
  b_j\le p_j\le a^2b_j\le\lambda b_j.
  \tag{7.7}\label{eq:nonexceptional-factor}
\]
Together with \Cref{prop:envelope-inversion}, this also gives $q_j\le b_j\le p_j$.

It remains to compare moments.  The total reciprocal mass of the $b_j$ is
$O_H(1)$ by \Cref{prop:envelope-inversion}, and the same is true for the $p_j$
by \eqref{eq:exceptional-b-mass} and \eqref{eq:nonexceptional-factor}.  Hence all
$r$-tuples containing at least one exceptional index contribute
\[
  O_{H,r,a}\left(\frac1{\log n}\right)=o_{H,\lambda}(1)
\]
to either $T_r^{(b)}(n)$ or $T_r^{(p)}(n)$.

For a nonexceptional tuple $I=\{j_1<\cdots<j_r\}$, write
\[
  b_I:=\prod_{j\in I}b_j,\qquad p_I:=\prod_{j\in I}p_j.
\]
By \eqref{eq:nonexceptional-factor},
\[
  b_I\le p_I\le\lambda^r b_I,\qquad
  \lambda^{-r}\frac1{b_I}\le\frac1{p_I}\le\frac1{b_I}.
\]
On tuples counted by both cutoffs, this changes the total reciprocal weight by
$O_{H,r}(\lambda-1)$, since the $r$-fold reciprocal mass is $O_H(1)$.  The
only cutoff discrepancy comes from tuples with
\[
  n/\lambda^r<b_I\le n.
\]
By the product-strip estimate proved from \Cref{lem:cell-reciprocal-mass} above,
these tuples have total $b$-reciprocal contribution $o_{H,\lambda}(1)$.  This
proves \eqref{eq:queued-bridge-moment}.
\end{proof}

\begin{proposition}[Diagonal parameter selection for the prime bridge]
\label{prop:prime-bridge-diagonalization}
Fix $0<\eps<1$.  There is an integer-valued function $H(n)\to\infty$ and,
for each $n$, comparison sequences
\[
  b_1^{(n)}\le\cdots\le b_K^{(n)},\qquad p_1^{(n)}<\cdots<p_K^{(n)}
\]
with the $p_j^{(n)}$ odd primes, such that
\[
  q_j\le b_j^{(n)}\le p_j^{(n)}\qquad (1\le j\le K),
\]
and, for every $1\le r\le4$,
\[
  T_r^{(b^{(n)})}(n)=J_r+o(1),
  \qquad
  T_r^{(p^{(n)})}(n)=J_r+o(1).
\]
\end{proposition}

\begin{proof}
Choose $H_m\to\infty$ increasing so that the excision estimate in
\Cref{prop:envelope-inversion} gives
\[
  |J_r^{(H_m)}-J_r|\le \frac{1}{4m}
  \qquad (1\le r\le4).
  \tag{7.8}\label{eq:diag-excision}
\]
For each fixed $H_m$ and $r$, choose a constant $C_{H_m,r}$ for the
$O_{H_m,r}(\lambda-1)$ term in \eqref{eq:queued-bridge-moment}.  Choose
$\lambda_m>1$ close enough to $1$ that
\[
  C_{H_m,r}(\lambda_m-1)\le \frac{1}{4m}
  \qquad (1\le r\le4),
  \tag{7.9}\label{eq:diag-lambda}
\]
and then choose $a_m>1$ with $a_m^2\le\lambda_m$.  Let $s_m=s(a_m)$ be the
queue length in \eqref{eq:queue-clear}.

We now choose $N_m$ recursively increasing.  Since $H_m,\lambda_m,a_m$ and
$s_m$ are fixed, all estimates used above are eventually valid, so we may
enlarge $N_m$ until, for every $n\ge N_m$, all of the following hold:
\[
  \xi_{H_m}(n)\le \frac1m,
  \tag{7.10a}\label{eq:diag-xi}
\]
\[
  |T_r^{(b^{(H_m)})}(n)-J_r^{(H_m)}|\le \frac{1}{4m}
  \qquad (1\le r\le4),
  \tag{7.10b}\label{eq:diag-envelope}
\]
\[
  |T_r^{(p^{(H_m)})}(n)-T_r^{(b^{(H_m)})}(n)|\le \frac{1}{2m}
  \qquad (1\le r\le4),
  \tag{7.10c}\label{eq:diag-bridge}
\]
\[
  n^{\alpha_{H_m-1}}\ge m.
  \tag{7.10d}\label{eq:diag-scale}
\]
Here $b^{(H_m)}$ is the comparison sequence from
\Cref{prop:envelope-inversion} with parameter $H_m$, and $p^{(H_m)}$ is the
prime sequence produced by \Cref{prop:queued-prime-rounding} with parameters
$H_m,\lambda_m,a_m$.  In addition, enlarge $N_m$ so that every fixed-ratio
prime number theorem estimate used in \eqref{eq:prime-bin-count} and every
fixed-ratio estimate used in \Cref{lem:cell-reciprocal-mass} and the product
strip bound holds with tolerance $1/m$ for the finitely many constants
arising from $H_m,a_m,s_m$ and $\lambda_m^r$, $1\le r\le4$.  The scale
condition \eqref{eq:diag-scale} is harmless because $H_m$ is fixed while
$n\to\infty$.

Define
\[
  H(n):=H_m\qquad\text{for }N_m\le n<N_{m+1},
\]
and use the corresponding sequences $b^{(H_m)}$ and $p^{(H_m)}$.  Then
$H(n)\to\infty$.  For $N_m\le n<N_{m+1}$, the telescope bounds are
\[
\begin{aligned}
  |T_r^{(b^{(H(n))})}(n)-J_r|
  &\le
  |T_r^{(b^{(H_m)})}(n)-J_r^{(H_m)}|
  +|J_r^{(H_m)}-J_r|  \\
  &\le \frac{1}{4m}+\frac{1}{4m}
  =\frac{1}{2m},
\end{aligned}
\]
and
\[
\begin{aligned}
  |T_r^{(p^{(H(n))})}(n)-J_r|
  &\le
  |T_r^{(p^{(H_m)})}(n)-T_r^{(b^{(H_m)})}(n)| \\
  &\quad
  +|T_r^{(b^{(H_m)})}(n)-J_r^{(H_m)}|
  +|J_r^{(H_m)}-J_r|  \\
  &\le \frac{1}{2m}+\frac{1}{4m}+\frac{1}{4m}
  =\frac1m .
\end{aligned}
\]
Thus $T_r^{(b^{(n)})}(n)=J_r+o(1)$ and
$T_r^{(p^{(n)})}(n)=J_r+o(1)$ for $1\le r\le4$.  The inequalities
$q_j\le b_j^{(n)}\le p_j^{(n)}$ come from
\Cref{prop:queued-prime-rounding}.
\end{proof}

\begin{theorem}[Prime-rounding bridge]\label{thm:prime-bridge}
Fix $0<\eps<1$, and let
\[
  K=\left\lfloor \frac{(1-\eps)n}{2\log n}\right\rfloor.
\]
There exists a choice of comparison sequences
\[
  b_1^{(n)}\le \cdots \le b_K^{(n)}
\]
from the construction of \Cref{prop:envelope-inversion}, and there exists an
increasing sequence of odd primes
\[
  p_1<\cdots<p_K
\]
such that
\[
  q_j \le p_j \qquad (1\le j\le K)
\]
and
\[
  T_r^{(b^{(n)})}(n)=J_r+o(1)
  \qquad (1\le r\le 4).
\]
Moreover the primes may be chosen so that, for each fixed $1\le r\le 4$,
\[
  T_r^{(p)}(n)=T_r^{(b^{(n)})}(n)+o(1)=J_r+o(1).
\]
\end{theorem}

\begin{proof}
\Cref{prop:prime-bridge-diagonalization} gives the required sequences and
moment limits.  Since $q_j\le b_j^{(n)}\le p_j^{(n)}$, in particular
$q_j\le p_j^{(n)}$ for every $j$.
\end{proof}

\subsection{The finite Bonferroni--4 theorem}

\begin{theorem}\label{thm:main-upper}
Under the piecewise-density prime-prefix strategy,
\[
  \L(n) \le \left(\frac{\Wfour}{2}+o(1)\right)n
  \le (0.1897123371+o(1))n < 0.19n.
\]
\end{theorem}

\begin{proof}
By \Cref{thm:prime-bridge}, there are a comparison sequence
$b_1\le\cdots\le b_K$ and an increasing odd-prime sequence $p_j$ with
$q_j\le p_j$ such that
\[
  T_r^{(b)}(n)=J_r+o(1)
  \qquad (1\le r\le 4).
\]
The same theorem gives
\[
  T_r^{(p)}(n)=J_r+o(1)
  \qquad (1\le r\le 4).
\]
Applying \Cref{thm:bonf-comp} with $\Lambda_r=J_r$ gives
\[
  \L(n)
  \le
  \frac n2\left(1-J_1+J_2-J_3+J_4+o(1)\right)
  =
  \left(\frac{\Wfour}{2}+o(1)\right)n.
\]
By \Cref{prop:wfour-certification},
\[
  \frac{\Wfour}{2}\le0.1897123371<0.19,
\]
so the theorem follows.
\end{proof}

\begin{remark}
The corresponding formal artifact verifies the endgame reduction: once the first four moment terms are sufficiently close to the certified constants $J_1,\dots,J_4$, the strict inequality $\L(n)<0.19n$ follows eventually.  Theorems~\ref{thm:bonf-comp} and \ref{thm:prime-bridge} supply those moment hypotheses.
\end{remark}
