\section{Conclusion}\label{sec:conclusion}

The results of this paper narrow the divisibility antichain saturation game in
two complementary ways.  On the upper-bound side, the main theorem gives
\[
  \L(n)<0.19n
\]
for all sufficiently large $n$, improving the elementary linear upper-bound
picture by using the local density of Shortener's legal-prime prefix and a
fourth-order Bonferroni comparison.  On the structural side, the shield
reduction and Theorem A show that short upper-half shield prefixes cannot prove
a linear game lower bound through the weighted shadow functional $\beta_n(P)$.

The conditional T2 theorem points toward a substantially larger lower-bound
scale, but it is deliberately stated under the safe-edge hypothesis because the
corresponding max-gain principle is false in general finite capture games.  The
finite graph, hypergraph, and embedding components are robust; the remaining
issue is precisely the safety property for the game-generated states.

Three obstructions in \Cref{sec:obstructions} explain why the next improvements
are unlikely to come from purely local relaxations, fixed shadow-cover
dichotomies, or separator-only strategies.  A sharper upper bound will need to
use dynamic information about the actual divisibility game, not merely the
static incidence geometry of low-rank shadows.  Conversely, an unconditional
lower bound beyond the classical prime-multiple argument must overcome
Shortener's ability to compress terminal antichains through odd-prime sieving.

The central question remains whether $\L(n)=o(n)$.  The methods here give new
constants, exact auxiliary structure, and a set of formal targets for future
work, but they do not settle that asymptotic dichotomy.
