\section{Conclusion}\label{sec:conclusion}

We have proved
\[
\left(\frac18-o(1)\right)\frac{n\log\log n}{\log n}
\le
L(n)
\le
\left(\frac{\Wfour}{2}+o(1)\right)n
=
(0.1897112+o(1))n
<
0.19n,
\]
and, through T2, we have also shown that the lower-bound side naturally
reaches the larger scale
\[
\frac{n(\log\log n)^2}{\log n}.
\]
The exact order of growth therefore remains open.  What has changed is the
shape of the remaining problem.  The present barrier inventory rules out a
large number of natural separator, packet, closure, and fan-based routes, so
the sharp-rate question is no longer just a matter of refining the first
successful heuristic.

Three directions now appear genuinely distinct.  The first is an improved upper
bound, ideally an $o(n)$ strategy that goes beyond the odd-prime-prefix family
of \Cref{sec:intermediate-upper,sec:main-upper}.  The second is a lower bound
that exceeds the current T2 scale and survives the fan, fiber, and same-core
obstructions of \Cref{sec:structural-negatives}.  The third is a clearer
understanding of restricted adversary classes and proof classes: theorems such
as \Cref{thm:theorem5,thm:theorem6,thm:separator-only,thm:sa-barrier} suggest
that the game mixes genuine combinatorial rigidity with strong sensitivity to
the exact modeling framework.

The first-player convention also remains mathematically relevant.  Throughout
this paper Prolonger moves first, matching the forum literature and all prior
private rounds in the repository.  A Shortener-first version of the game could
have a different asymptotic behavior and deserves separate study.
