\section{Conditional Proof of the T2 Lower Bound}\label{app:t2-proof}

This appendix proves the conditional lower bound in \Cref{thm:t2}.  The proof
is self-contained: all target families, auxiliary games, weights, activation
rules, deletion errors, and asymptotic estimates are defined below.  The
opening counterexample explains why the finite safe-edge hypothesis is stated
explicitly rather than hidden inside a max-gain argument.

Throughout this appendix $n$ is large, $0<\delta<1/4$ is fixed, and
\[
  Y:=n^\delta.
\]
Let $\mathcal P_Y$ be the set of odd primes at most $Y$.  For
$a<c$ in $\mathcal P_Y$, put
\[
  I_{a,c}:=\left(\frac{n}{2ac},\frac{n}{ac}\right],
  \qquad
  B_{a,c}:=I_{a,c}\cap\PP,
\]
and define the target family
\[
  \mathcal T
  :=
  \{\,acb:\ a<c,\ a,c\in\mathcal P_Y,\ b\in B_{a,c}\,\}.
\]
For large $n$, every such $b$ is greater than $Y$: indeed
$b>n/(2Y^2)=\frac12 n^{1-2\delta}>Y$.  Thus $a,c,b$ are distinct primes and
each target $acb$ lies in $(n/2,n]$.

\begin{proposition}[Max-gain domination is false in rank three]
\label{prop:t2-max-gain-counterexample}
The following finite scored rank-$3$ capture state has a unique max-gain Maker
move, but Breaker can answer that move by deleting one uncaptured vertex and
make the scaled potential decrease.
\end{proposition}

\begin{proof}
Let the already-captured vertices be
\[
  C=\{z_{ij}:1\le i,j\le 3\},
\]
and let $u_1,u_2,u_3,v$ be uncaptured.  There are no deleted or scored edges.
The live edges are
\[
  f=\{u_1,u_2,u_3\},\qquad w(f)=9,
\]
and, for $1\le i,j\le 3$,
\[
  e_{ij}=\{v,u_i,z_{ij}\},\qquad w(e_{ij})=4.
\]
For a live edge $e$, write $\Phi(e)=2^{|e\cap C|}w(e)$ and
$Q=8S+\sum\Phi(e)$.

Before Maker moves, $\Phi(f)=9$ and $\Phi(e_{ij})=8$ for all $i,j$.  If Maker
plays $f$, then the score contribution of $f$ changes by
$8w(f)-\Phi(f)=72-9=63$, and each of the nine edges $e_{ij}$ doubles from
$8$ to $16$.  Hence
\[
  \Delta(f)=63+9\cdot 8=135.
\]
After this move, the vertex $v$ is still uncaptured, and deleting $v$ removes
all nine edges $e_{ij}$, now of potential $16$ each.  The Breaker loss is
\[
  9\cdot 16=144>135.
\]
Thus the full round decreases $Q$.

It remains only to check that $f$ is the unique max-gain move.  If Maker plays
some $e_{ij}$, its own score gain is $8\cdot4-8=24$.  The edge $f$ doubles
from $9$ to $18$, giving gain $9$.  The two other edges with the same $u_i$
gain $24$ each, and the six edges with the other two $u$-vertices gain $8$
each.  Therefore
\[
  \Delta(e_{ij})=24+9+2\cdot24+6\cdot8=129<135.
\]
So the unique max-gain move is $f$, and it does not dominate the subsequent
vertex deletion at $v$.
\end{proof}

\begin{proposition}[Conditional finite scaled capture]\label{prop:t2-finite-capture}
Consider a finite weighted incidence game of rank at most $3$ with the scaled
potential
\[
  Q:=8S+\sum_{e\text{ live}}2^{|e\cap C|}w(e),
\]
where $C$ is the current captured-vertex set and $S$ is the total scored
weight.  In the graph variant, Breaker may delete one unclaimed live edge; in
the scored hypergraph variant, Breaker may score one live edge.

Assume the following safe-edge hypothesis: at every reachable pre-Maker state
with at least one positive-weight live edge, Maker has a legal live edge $f$
such that, after Maker plays $f$, every legal Breaker reply leaves $Q$ at least
as large as it was before Maker's move.

Under this hypothesis, if the game is continued until no positive-weight live
edge remains, the final claimed or scored weight is at least one eighth of the
initial total edge-weight:
\[
  S_{\mathrm{fin}}
  \ge
  \frac18\sum_{e}w(e).
\]
\end{proposition}

\begin{proof}
Maker always chooses an edge supplied by the safe-edge hypothesis.  By
definition of that hypothesis, $Q$ is nondecreasing after every full
Maker--Breaker round.

Initially $C=\varnothing$, $S=0$, and all initial edges are live, so
\[
  Q_0=\sum_e w(e).
\]
At terminal time there is no positive-weight live edge, hence
$Q_{\mathrm{fin}}=8S_{\mathrm{fin}}$.  Therefore
\[
  8S_{\mathrm{fin}}=Q_{\mathrm{fin}}\ge Q_0=\sum_e w(e),
\]
which is the claimed one-eighth bound.

For the graph variant, a Breaker edge-deletion reply is included in the
safe-edge hypothesis.  For the scored hypergraph variant, a Breaker scored-edge
reply is harmless whenever it occurs, since it changes $Q$ by
$8w(e)-2^{|e\cap C|}w(e)\ge0$ for rank at most $3$; the only nontrivial part of
the hypothesis is therefore the post-Maker vertex-deletion bound.
\end{proof}

\begin{proposition}[Initial target mass]\label{prop:t2-initial-mass}
For every fixed $0<\delta<1/4$,
\[
  W_0
  :=
  \sum_{\substack{a<c\\a,c\in\mathcal P_Y}} |B_{a,c}|
  \gg_\delta
  \frac{n(\log\log n)^2}{\log n}.
\]
\end{proposition}

\begin{proof}
Since $ac\le Y^2=n^{2\delta}$, the interval endpoint
$X_{a,c}:=n/(ac)$ satisfies $X_{a,c}\ge n^{1-2\delta}\to\infty$.  By the prime
number theorem, uniformly for all such pairs and all sufficiently large $n$,
\[
  \pi(X_{a,c})-\pi(X_{a,c}/2)
  \ge
  \kappa_\delta \frac{X_{a,c}}{\log n}
  =
  \kappa_\delta \frac{n}{ac\log n}
\]
for some positive constant $\kappa_\delta$.  Therefore
\[
  W_0
  \ge
  \kappa_\delta\frac{n}{\log n}
  \sum_{\substack{a<c\\a,c\in\mathcal P_Y}}\frac1{ac}.
\]
Mertens' theorem for primes gives
\[
  \sum_{p\in\mathcal P_Y}\frac1p
  =
  \log\log Y+O(1)
  =
  \log\log n+O_\delta(1),
\]
and $\sum_p p^{-2}<\infty$.  Hence
\[
  \sum_{a<c\in\mathcal P_Y}\frac1{ac}
  =
  \frac12\left[
    \left(\sum_{p\in\mathcal P_Y}\frac1p\right)^2
    -
    \sum_{p\in\mathcal P_Y}\frac1{p^2}
  \right]
  =
  \left(\frac12+o(1)\right)(\log\log n)^2.
\]
Combining the last two displays proves the claim.
\end{proof}

\begin{proposition}[Residual divisibility embedding]\label{prop:t2-residual-embedding}
Let $\mathcal T_*$ be any subfamily of targets $t=acb\in\mathcal T$ such that,
for every $t=acb\in\mathcal T_*$, the numbers $a$, $c$, and $ac$ are already
unavailable as legal moves.  Attach to $t$ the three slot labels
\[
  b,\qquad ab,\qquad cb
\]
and let $e_t:=\{b,ab,cb\}$.  Then the residual divisibility game on
$\mathcal T_*$ is at least as favorable to Prolonger as the scored rank-$3$
hypergraph game on the hyperedges $\{e_t:t\in\mathcal T_*\}$:
\begin{enumerate}
  \item the only future moves that can make $t=acb$ illegal are
    $b$, $ab$, $cb$, and $t$ itself;
  \item playing $b$, $ab$, or $cb$ deletes exactly the residual targets whose
    hyperedges contain that slot;
  \item playing the exact target $t$ kills no other target in $\mathcal T_*$,
    and is therefore a scored-edge move;
  \item every live hyperedge corresponds to a legal actual move $t$.
\end{enumerate}
\end{proposition}

\begin{proof}
Fix $t=acb\in\mathcal T_*$.  Because $t>n/2$, no proper multiple of $t$ lies in
$\{2,\dots,n\}$.  Thus a future move can make $t$ illegal only by being $t$
itself or a proper divisor of $t$.  The positive divisors are
\[
  1,\ a,\ c,\ ac,\ b,\ ab,\ cb,\ acb.
\]
The divisor $1$ is not a move, while $a$, $c$, and $ac$ are unavailable by
hypothesis.  This proves the first assertion.

For slot incidence, suppose another target is $t'=a'c'b'$.  Since
$b,b'>Y\ge a,a',c,c'$, the divisibility $b\mid t'$ holds iff $b=b'$.  Thus a
move $b$ kills exactly the targets in the $b$-fiber.  Similarly, if
$ab\mid a'c'b'$, the large prime factor forces $b=b'$, and after cancellation
$a$ must be $a'$ or $c'$.  This is exactly the condition that the slot $ab$
belongs to $e_{t'}$.  The proof for $cb$ is identical.

If two targets $t,u$ in $\mathcal T_*$ are comparable, say $t\mid u$, then
$u$ is a multiple of $t$ lying in $(n/2,n]$.  The next positive multiple of
$t$ after $t$ is $2t>n$, so $u=t$.  Hence distinct targets are pairwise
incomparable, and playing an exact target scores only that target.

Finally, if $e_t$ is live in the slot hypergraph, then none of $b$, $ab$, $cb$,
or $t$ has been played.  The only other proper divisors of $t$ are
$1,a,c,ac$, and these are either not moves or already unavailable.  There is no
proper multiple of $t$ on the board.  Therefore no played number is comparable
with $t$, so the actual move $t$ is legal.  This proves the comparison.
\end{proof}

\begin{proposition}[Activation-stage potential]\label{prop:t2-activation-potential}
During activation, let each unclaimed pair edge $e=(a,c)$ carry the current
token set $B_e(t)$ of primes $b\in B_{a,c}$ for which the target $acb$ has not
yet been killed.  Write $w_t(e):=|B_e(t)|$.

Assume the safe-edge hypothesis of \Cref{prop:t2-finite-capture} for the
activation graph states generated below.  Prolonger plays as follows.  In each
activation round, among pair edges with positive current token weight, he
chooses a safe edge supplied by that hypothesis; if $e=(a,c)$ is chosen, he
plays one live target $acb$ with $b\in B_e(t)$.  This scores one actual move,
claims the pair edge $e$, captures the vertices $a$ and $c$, and leaves the
remaining live tokens on that secured pair for the residual phase.

Let $S_t$ be the number of activation targets already played by Prolonger, and
define
\[
  Q_t
  :=
  S_t+\sum_e \phi_t(e),
\]
where
\[
  \phi_t(e)=
  \begin{cases}
    \frac18 w_t(e),& e\text{ unclaimed and neither endpoint captured},\\[1mm]
    \frac14 w_t(e),& e\text{ unclaimed and one endpoint captured},\\[1mm]
    \frac12 w_t(e),& e\text{ unclaimed and two endpoints captured},\\[1mm]
    w_t(e),& e\text{ claimed},\\[1mm]
    0,& e\text{ deleted}.
  \end{cases}
\]
Let $E$ be the total number of target tokens deleted during activation by
Shortener moves not modeled as graph vertex deletions $a$ or graph edge
deletions $ac$.  At the end of activation,
\[
  Q_{\mathrm{end}}\ge \frac{W_0}{8}-E.
\]
Equivalently,
\[
  S_{\mathrm{end}}
  +
  \sum_{e\text{ secured}} w_{\mathrm{end}}(e)
  \ge
  \frac{W_0}{8}-E.
\]
\end{proposition}

\begin{proof}
First ignore off-model token deletions.  Conditional on the safe-edge
hypothesis, the activation process is exactly the rank-$2$ graph game of
\Cref{prop:t2-finite-capture}, with one harmless
bookkeeping change: when Prolonger claims an edge $e$, he consumes one token
from $e$ and adds it immediately to the score $S_t$.  If the coefficient of
$e$ before the move is $\gamma\in\{1/8,1/4,1/2\}$, the contribution of $e$
changes from $\gamma w_t(e)$ to
\[
  1+(w_t(e)-1)=w_t(e),
\]
exactly as if the edge had become claimed with full weight.  All other
incident edges change as in the graph game.  Thus the scaled potential
argument gives $Q_{\mathrm{end}}\ge W_0/8$ when every harmful Shortener move is
a graph deletion.

Now restore all actual Shortener moves.  A token $acb$ is deleted precisely
when Shortener plays one of its still-available harmful divisors or the target
itself.  Deleting one live token can reduce $Q_t$ by at most $1$, since every
coefficient appearing in the definition of $\phi_t(e)$ is at most $1$.
Therefore all off-model deletions together reduce the lower bound by at most
$E$, giving
\[
  Q_{\mathrm{end}}\ge W_0/8-E.
\]
At the end of activation, a positive-weight edge is either secured or deleted,
so $Q_{\mathrm{end}}$ is exactly the activation score plus the residual live
target weight on secured pairs.
\end{proof}

\begin{proposition}[Activation deletion budget]\label{prop:t2-deletion-budget}
For fixed $0<\delta<1/4$, the off-model deletion count from
\Cref{prop:t2-activation-potential} satisfies
\[
  E\ll \frac{Y^4}{\log^4 Y}
  =
  o\!\left(\frac{n(\log\log n)^2}{\log n}\right).
\]
\end{proposition}

\begin{proof}
There is at most one activation round per small-prime pair, so the number of
rounds is
\[
  R\le \binom{|\mathcal P_Y|}{2}
  \ll \frac{Y^2}{\log^2Y}.
\]
We bound the number of live tokens an off-model Shortener move can delete.

If Shortener plays a large prime $b$, then for each pair $(a,c)$ there is at
most one token $acb$ using that $b$.  Hence the move deletes at most
$O(Y^2/\log^2Y)$ tokens.  If Shortener plays a lateral semiprime $pb$ with
$p\le Y$ and $b>Y$ prime, the killed targets have the form $pcb$ with the
third small prime varying, so there are at most $O(Y/\log Y)$ of them.  If
Shortener plays an exact target $acb$, exactly one token is deleted.

The worst of these bounds is the large-prime bound.  Across $R$ activation
rounds,
\[
  E\ll R\frac{Y^2}{\log^2Y}
  \ll \frac{Y^4}{\log^4Y}.
\]
Since $Y=n^\delta$,
\[
  \frac{Y^4/\log^4Y}{n(\log\log n)^2/\log n}
  \ll_\delta
  \frac{n^{4\delta-1}}{(\log n)^3(\log\log n)^2}
  \to 0
\]
because $4\delta-1<0$.
\end{proof}

\begin{proposition}[Residual mass on secured pairs]\label{prop:t2-residual-mass}
At the end of activation, the secured pairs carry residual live target weight
\[
  M:=
  \sum_{e\text{ secured}} w_{\mathrm{end}}(e)
  \gg_\delta
  \frac{n(\log\log n)^2}{\log n}.
\]
\end{proposition}

\begin{proof}
By \Cref{prop:t2-activation-potential},
\[
  S_{\mathrm{end}}+M\ge \frac{W_0}{8}-E.
\]
The activation score is at most the number of small-prime pairs:
\[
  S_{\mathrm{end}}\le R\ll \frac{Y^2}{\log^2Y}
  =
  o\!\left(\frac{n(\log\log n)^2}{\log n}\right),
\]
because $2\delta<1$.  The deletion budget $E$ is negligible by
\Cref{prop:t2-deletion-budget}, while $W_0$ has the required lower bound by
\Cref{prop:t2-initial-mass}.  Subtracting the two negligible terms gives the
claim.
\end{proof}

\begin{proposition}[Conditional T2 lower bound]\label{prop:t2-final}
Assume the safe-edge hypothesis of \Cref{prop:t2-finite-capture} for the
activation graph states and for the residual slot-hypergraph states generated
by the construction above.
For every fixed $0<\delta<1/4$ there is $c_\delta>0$ such that
\[
  \L(n)\ge c_\delta\frac{n(\log\log n)^2}{\log n}
\]
for all sufficiently large $n$.
\end{proposition}

\begin{proof}
After activation, restrict to the residual live targets lying over secured
pairs.  Their total weight is $M$, as in
\Cref{prop:t2-residual-mass}.  For each secured pair $(a,c)$, the activation
move made $a$, $c$, and $ac$ unavailable.  Therefore
\Cref{prop:t2-residual-embedding} compares the remaining divisibility game to a
scored rank-$3$ slot hypergraph whose total edge weight is $M$.

Under the residual safe-edge hypothesis, \Cref{prop:t2-finite-capture} gives a
strategy that forces scored residual target weight at least $M/8$ in this
hypergraph model.  The comparison proposition says that every such scored
hypergraph move is a genuine actual game move, and that the actual game gives
Prolonger no fewer legal options than the model.  Hence the number of residual
moves after activation is at least $M/8$.  Since
$M\gg_\delta n(\log\log n)^2/\log n$, the same lower bound holds for the total
game length, conditional on the stated safe-edge hypothesis.

Choosing any fixed $\delta<1/4$, for instance $\delta=1/8$, gives an absolute
constant $c>0$ and proves \Cref{thm:t2}.
\end{proof}
