\section{Deferred Proofs}\label{app:deferred-proofs}

\subsection{Conditional proof of the T2 lower bound}\label{app:t2-proof}

This appendix proves the conditional lower bound in \Cref{thm:t2}.  The proof
is self-contained: all target families, auxiliary games, weights, activation
rules, deletion errors, and asymptotic estimates are defined below.  The
opening counterexamples explain why the restricted finite safe-edge hypothesis
is stated explicitly rather than hidden inside a max-gain argument.

Throughout this appendix $n$ is large, $0<\delta<1/4$ is fixed, and
\[
  Y:=n^\delta.
\]
Let $\mathcal P_Y$ be the set of odd primes at most $Y$.  For
$a<c$ in $\mathcal P_Y$, put
\[
  I_{a,c}:=\left(\frac{n}{2ac},\frac{n}{ac}\right],
  \qquad
  B_{a,c}:=I_{a,c}\cap\PP,
\]
and define the target family
\[
  \mathcal T
  :=
  \{\,acb:\ a<c,\ a,c\in\mathcal P_Y,\ b\in B_{a,c}\,\}.
\]
For large $n$, every such $b$ is greater than $Y$: indeed
$b>n/(2Y^2)=\frac12 n^{1-2\delta}>Y$.  Thus $a,c,b$ are distinct primes and
each target $acb$ lies in $(n/2,n]$.

\begin{proposition}[Max-gain domination is false in rank three]
\label{prop:t2-max-gain-counterexample}
The following finite scored rank-$3$ capture state has a unique max-gain Maker
move, but Breaker can answer that move by deleting one uncaptured vertex and
make the scaled potential decrease.
\end{proposition}

\begin{proof}
Let the already-captured vertices be
\[
  C=\{z_{ij}:1\le i,j\le 3\},
\]
and let $u_1,u_2,u_3,v$ be uncaptured.  There are no deleted or scored edges.
The live edges are
\[
  f=\{u_1,u_2,u_3\},\qquad w(f)=9,
\]
and, for $1\le i,j\le 3$,
\[
  e_{ij}=\{v,u_i,z_{ij}\},\qquad w(e_{ij})=4.
\]
For a live edge $e$, write $\Phi(e)=2^{|e\cap C|}w(e)$ and
$Q=8S+\sum\Phi(e)$.

Before Maker moves, $\Phi(f)=9$ and $\Phi(e_{ij})=8$ for all $i,j$.  If Maker
plays $f$, then the score contribution of $f$ changes by
$8w(f)-\Phi(f)=72-9=63$, and each of the nine edges $e_{ij}$ doubles from
$8$ to $16$.  Hence
\[
  \Delta(f)=63+9\cdot 8=135.
\]
After this move, the vertex $v$ is still uncaptured, and deleting $v$ removes
all nine edges $e_{ij}$, now of potential $16$ each.  The Breaker loss is
\[
  9\cdot 16=144>135.
\]
Thus the full round decreases $Q$.

It remains only to check that $f$ is the unique max-gain move.  If Maker plays
some $e_{ij}$, its own score gain is $8\cdot4-8=24$.  The edge $f$ doubles
from $9$ to $18$, giving gain $9$.  The two other edges with the same $u_i$
gain $24$ each, and the six edges with the other two $u$-vertices gain $8$
each.  Therefore
\[
  \Delta(e_{ij})=24+9+2\cdot24+6\cdot8=129<135.
\]
So the unique max-gain move is $f$, and it does not dominate the subsequent
vertex deletion at $v$.
\end{proof}

\begin{proposition}[\texorpdfstring{$K_4$}{K4}-fiber refutation in the residual arithmetic game]
\label{prop:t2-safe-edge-refutation}
For every fixed $0<\delta<1/4$ and all sufficiently large $n$, the residual
slot hypergraph $G(n,\delta)$ contains a reachable pre-Maker state at which
every legal Maker move admits a legal Breaker reply that strictly decreases
the scaled potential $Q$.  Hence the general safe-edge hypothesis is false even
inside the arithmetic games $G(n,\delta)$.
\end{proposition}

\begin{proof}
Here $G(n,\delta)$ is the scored rank-three slot hypergraph with edges
\[
  e_{a,c,b}:=\{b,ab,cb\},
  \qquad
  a<c,\quad a,c\in\mathcal P_Y,\quad b\in B_{a,c},
\]
each of weight $1$.

Choose the four fixed small primes $13,17,19,23$.  Their pairwise products are
\[
  13\cdot17=221,\quad 13\cdot19=247,\quad 13\cdot23=299,\quad
  17\cdot19=323,\quad 17\cdot23=391,\quad 19\cdot23=437.
\]
All six products lie between $221$ and $437$, and $2\cdot221=442>437$.  For
sufficiently large $n$, since $23\le n^\delta=Y$, all four primes lie in
$\mathcal P_Y$.  By the prime number theorem, the interval
\[
  \left(\frac{n}{442},\frac{n}{437}\right]
\]
contains a prime $q$ for all sufficiently large $n$.  Also $q>Y$ for large
$n$, since $\delta<1/4$.

For every pair $a<c$ among $\{13,17,19,23\}$, we have
\[
  q>\frac n{442}\ge\frac n{2ac}
  \qquad\text{and}\qquad
  q\le\frac n{437}\le\frac n{ac},
\]
because $ac\ge221$ and $ac\le437$.  Hence $q\in B_{a,c}$ for all six pairs,
and the six edges
\[
  e_{a,c}:=\{q,aq,cq\}
\]
all occur in $G(n,\delta)$.  They form a $K_4$-fiber over the common slot $q$.

We next reach a state in which only these six edges are live and no vertex in
them has yet been captured.  While any other edge is live, Maker uses the
alternate-scoring move to score that exact target without adding slot vertices
to $C$.  Any edge outside this six-edge family has at least one slot outside
\[
  U_{\mathrm{fib}}:=\{q,13q,17q,19q,23q\},
\]
so Breaker deletes such an outside slot.  This never harms the six desired
edges.  Repeating this finite operation leaves exactly the six $K_4$-fiber
edges live, with $C=\varnothing$.

From that state, play two legal rounds.  First Maker captures
\[
  e_{13,17}=\{q,13q,17q\},
\]
so $q,13q,17q\in C$, and Breaker deletes the live edge $e_{13,19}$.  Next
Maker captures
\[
  e_{19,23}=\{q,19q,23q\},
\]
so $q,13q,17q,19q,23q\in C$, and Breaker deletes the live edge $e_{13,23}$.

At the next pre-Maker state, the only remaining live edges from this fiber are
\[
  e_{17,19}=\{q,17q,19q\},
  \qquad
  e_{17,23}=\{q,17q,23q\}.
\]
Both have all three vertices in $C$, so $\Phi(e)=2^3\cdot1=8$ for each.  There
are no other live edges by construction.

Maker has only two possible live edges to play.  If Maker plays $e_{17,19}$,
by ordinary capture or by alternate scoring, then the change in $Q$ is
\[
  +8\cdot1-8=0,
\]
because $S$ increases by $1$, the edge of potential $8$ is removed, and no new
vertex is added to $C$.  The remaining live edge $e_{17,23}$ still contributes
$8$.  Breaker then deletes $e_{17,23}$, decreasing $Q$ by $8$.  Thus
$Q_{\mathrm{after}}=Q_{\mathrm{before}}-8$.  The same argument holds if Maker
instead plays $e_{17,23}$.

Therefore this reachable pre-Maker state has the claimed property: every legal
Maker move admits a legal Breaker reply that strictly decreases $Q$.
Note that Breaker's final reply here is an unscored edge deletion, adding
$e_{17,23}$ to $D_E$, not a scored-edge play; under the scored-edge rule, the
same move would change $Q$ by $0$, not by $-8$.  The refutation shows that the
general safe-edge hypothesis fails even when Breaker has access to the
unscored-edge-deletion move, which is the regime relevant to the rank-$3$
residual hypergraph game.
\end{proof}

\begin{proposition}[Conditional finite scaled capture]\label{prop:t2-finite-capture}
Consider a finite weighted incidence game of rank at most $3$ with the scaled
potential
\[
  Q:=8S+\sum_{e\text{ live}}2^{|e\cap C|}w(e),
\]
where $C$ is the current captured-vertex set and $S$ is the total scored
weight.  In each full Maker--Breaker round, Breaker may play any one of:
\begin{enumerate}
  \item[(i)] a vertex deletion: add an uncaptured vertex
    $v\in V\setminus C$ to $D_V$;
  \item[(ii)] an unscored edge deletion: add one currently live edge $e$ to
    $D_E$, available in both the graph and scored-hypergraph variants;
  \item[(iii)] a scored-edge reply: add one currently live edge $e$ to $K$ and
    increment $S$ by $w(e)$, available only in the scored-hypergraph variant.
\end{enumerate}

The general safe-edge hypothesis stated below is provably false even for
$G(n,\delta)$; see \Cref{prop:t2-safe-edge-refutation}.  In this paper the
finite-capture proposition is used only under the restricted hypothesis that
the same property holds for states actually generated by the activation and
residual strategies in \Cref{prop:t2-activation-potential,prop:t2-final}.  This
restricted hypothesis remains open.

Assume the following restricted safe-edge hypothesis: at every pre-Maker state
generated by the strategy under consideration with at least one positive-weight
live edge, Maker has a legal live edge $f$ such that every legal Breaker reply
from (i)--(iii) applicable to the current variant leaves $Q$ at least as large
as it was before Maker's move.

Under this restricted hypothesis, if the game is continued until no
positive-weight live edge remains, the final claimed or scored weight is at
least one eighth of the initial total edge-weight:
\[
  S_{\mathrm{fin}}
  \ge
  \frac18\sum_{e}w(e).
\]
\end{proposition}

\begin{proof}
Maker always chooses an edge supplied by the restricted safe-edge hypothesis.
By
definition of that hypothesis, $Q$ is nondecreasing after every full
Maker--Breaker round.

Initially $C=\varnothing$, $S=0$, and all initial edges are live, so
\[
  Q_0=\sum_e w(e).
\]
At terminal time there is no positive-weight live edge, hence
$Q_{\mathrm{fin}}=8S_{\mathrm{fin}}$.  Therefore
\[
  8S_{\mathrm{fin}}=Q_{\mathrm{fin}}\ge Q_0=\sum_e w(e),
\]
which is the claimed one-eighth bound.

For the graph variant, a Breaker edge-deletion reply is included in the
restricted safe-edge hypothesis.  For the scored hypergraph variant, a Breaker
scored-edge reply is harmless whenever it occurs, since it changes $Q$ by
$8w(e)-2^{|e\cap C|}w(e)\ge0$ for rank at most $3$; the only nontrivial part of
the hypothesis is therefore the post-Maker vertex-deletion bound.
\end{proof}

\begin{proposition}[Initial target mass]\label{prop:t2-initial-mass}
For every fixed $0<\delta<1/4$,
\[
  W_0
  :=
  \sum_{\substack{a<c\\a,c\in\mathcal P_Y}} |B_{a,c}|
  \gg_\delta
  \frac{n(\log\log n)^2}{\log n}.
\]
\end{proposition}

\begin{proof}
Since $ac\le Y^2=n^{2\delta}$, the interval endpoint
$X_{a,c}:=n/(ac)$ satisfies $X_{a,c}\ge n^{1-2\delta}\to\infty$.  By the prime
number theorem, uniformly for all such pairs and all sufficiently large $n$,
\[
  \pi(X_{a,c})-\pi(X_{a,c}/2)
  \ge
  \kappa_\delta \frac{X_{a,c}}{\log n}
  =
  \kappa_\delta \frac{n}{ac\log n}
\]
for some positive constant $\kappa_\delta$.  Therefore
\[
  W_0
  \ge
  \kappa_\delta\frac{n}{\log n}
  \sum_{\substack{a<c\\a,c\in\mathcal P_Y}}\frac1{ac}.
\]
Mertens' theorem for primes gives
\[
  \sum_{p\in\mathcal P_Y}\frac1p
  =
  \log\log Y+O(1)
  =
  \log\log n+O_\delta(1),
\]
and $\sum_p p^{-2}<\infty$.  Hence
\[
  \sum_{a<c\in\mathcal P_Y}\frac1{ac}
  =
  \frac12\left[
    \left(\sum_{p\in\mathcal P_Y}\frac1p\right)^2
    -
    \sum_{p\in\mathcal P_Y}\frac1{p^2}
  \right]
  =
  \left(\frac12+o(1)\right)(\log\log n)^2.
\]
Combining the last two displays proves the claim.
\end{proof}

\begin{proposition}[Residual divisibility embedding]\label{prop:t2-residual-embedding}
Let $\mathcal T_*$ be a subfamily of targets $t=acb\in\mathcal T$ with the
following secured-pair origin.  For every $t=acb\in\mathcal T_*$, there is a
securing target
\[
  t_0(a,c)=acb_0\in\mathcal T,\qquad b_0\ne b,
\]
which has already been played, making $a$, $c$, and $ac$ unavailable as move
options; and no other earlier move is comparable with any
$t\in\mathcal T_*$.  Attach to $t$ the three slot labels
\[
  b,\qquad ab,\qquad cb
\]
and let $e_t:=\{b,ab,cb\}$.  Then the residual divisibility game on
$\mathcal T_*$ is at least as favorable to Prolonger as the scored rank-$3$
hypergraph game on the hyperedges $\{e_t:t\in\mathcal T_*\}$:
\begin{enumerate}
  \item the only future moves that can make $t=acb$ illegal are
    $b$, $ab$, $cb$, and $t$ itself;
  \item playing $b$, $ab$, or $cb$ deletes exactly the residual targets whose
    hyperedges contain that slot;
  \item playing the exact target $t$ kills no other target in $\mathcal T_*$,
    and is therefore a scored-edge move;
  \item every live hyperedge corresponds to a legal actual move $t$.
\end{enumerate}
\end{proposition}

\begin{proof}
Fix $t=acb\in\mathcal T_*$.  Because $t>n/2$, no proper multiple of $t$ lies in
$\{2,\dots,n\}$.  Thus a future move can make $t$ illegal only by being $t$
itself or a proper divisor of $t$.  The positive divisors are
\[
  1,\ a,\ c,\ ac,\ b,\ ab,\ cb,\ acb.
\]
The divisor $1$ is not a move, while $a$, $c$, and $ac$ are unavailable by
the played securing target $t_0(a,c)$.  This proves the first assertion.

For slot incidence, suppose another target is $t'=a'c'b'$.  Since
$b,b'>Y\ge a,a',c,c'$, the divisibility $b\mid t'$ holds iff $b=b'$.  Thus a
move $b$ kills exactly the targets in the $b$-fiber.  Similarly, if
$ab\mid a'c'b'$, the large prime factor forces $b=b'$, and after cancellation
$a$ must be $a'$ or $c'$.  This is exactly the condition that the slot $ab$
belongs to $e_{t'}$.  The proof for $cb$ is identical.

If two targets $t,u$ in $\mathcal T_*$ are comparable, say $t\mid u$, then
$u$ is a multiple of $t$ lying in $(n/2,n]$.  The next positive multiple of
$t$ after $t$ is $2t>n$, so $u=t$.  Hence distinct targets are pairwise
incomparable, and playing an exact target scores only that target.

Finally, if $e_t$ is live in the slot hypergraph, then none of $b$, $ab$, $cb$,
or $t$ has been played.  The only other proper divisors of $t$ are
$1,a,c,ac$, and these are either not moves or are unavailable because of the
played securing target $t_0(a,c)$.  The securing target is a distinct target
larger than $n/2$, hence is incomparable with $t$, and there is no proper
multiple of $t$ on the board.  By hypothesis, no other earlier move is
comparable with any target in $\mathcal T_*$.  Therefore no played number is
comparable with $t$, so the actual move $t$ is legal.  This proves the
comparison.
\end{proof}

\begin{proposition}[Activation-stage potential]\label{prop:t2-activation-potential}
During activation, let each unclaimed pair edge $e=(a,c)$ carry the current
token set $B_e(t)$ of primes $b\in B_{a,c}$ for which the target $acb$ has not
yet been killed.  Write $w_t(e):=|B_e(t)|$.

Assume the restricted safe-edge hypothesis of
\Cref{prop:t2-finite-capture} for the activation graph states generated below.
Prolonger plays as follows.  In each activation round, among pair edges with
positive current token weight, he chooses a safe edge supplied by that
hypothesis; if $e=(a,c)$ is chosen, he plays one live target $acb$ with
$b\in B_e(t)$.  This scores one actual move, claims the pair edge $e$, captures
the vertices $a$ and $c$, and leaves the remaining live tokens on that secured
pair for the residual phase.

Let $S_t$ be the number of activation targets already played by Prolonger, and
define
\[
  Q_t
  :=
  S_t+\sum_e \phi_t(e),
\]
where
\[
  \phi_t(e)=
  \begin{cases}
    \frac18 w_t(e),& e\text{ unclaimed and neither endpoint captured},\\[1mm]
    \frac14 w_t(e),& e\text{ unclaimed and one endpoint captured},\\[1mm]
    \frac12 w_t(e),& e\text{ unclaimed and two endpoints captured},\\[1mm]
    w_t(e),& e\text{ claimed},\\[1mm]
    0,& e\text{ deleted}.
  \end{cases}
\]
Let $E$ be the total number of target tokens deleted during activation by
Shortener moves not modeled as graph vertex deletions $a$ or graph edge
deletions $ac$.  Here $E$ counts the total number of live target tokens deleted
by off-model Shortener moves during activation, not the number of such moves:
a single off-model move can delete multiple tokens, and $E$ tallies deletions,
not move events.  At the end of activation,
\[
  Q_{\mathrm{end}}\ge \frac{W_0}{8}-E.
\]
Equivalently,
\[
  S_{\mathrm{end}}
  +
  \sum_{e\text{ secured}} w_{\mathrm{end}}(e)
  \ge
  \frac{W_0}{8}-E.
\]
\end{proposition}

\begin{proof}
First ignore off-model token deletions.  Conditional on the restricted safe-edge
hypothesis, the activation process is exactly the rank-$2$ graph game of
\Cref{prop:t2-finite-capture}, with one harmless
bookkeeping change: when Prolonger claims an edge $e$, he consumes one token
from $e$ and adds it immediately to the score $S_t$.  If the coefficient of
$e$ before the move is $\gamma\in\{1/8,1/4,1/2\}$, the contribution of $e$
changes from $\gamma w_t(e)$ to
\[
  1+(w_t(e)-1)=w_t(e),
\]
exactly as if the edge had become claimed with full weight.  All other
incident edges change as in the graph game.  Thus the scaled potential
argument gives $Q_{\mathrm{end}}\ge W_0/8$ when every harmful Shortener move is
a graph deletion.

Now restore all actual Shortener moves.  A token $acb$ is deleted precisely
when Shortener plays one of its still-available harmful divisors or the target
itself.  Deleting one live token can reduce $Q_t$ by at most $1$, since every
coefficient appearing in the definition of $\phi_t(e)$ is at most $1$.
Therefore all off-model deletions together reduce the lower bound by at most
$E$, giving
\[
  Q_{\mathrm{end}}\ge W_0/8-E.
\]
At the end of activation, a positive-weight edge is either secured or deleted,
so $Q_{\mathrm{end}}$ is exactly the activation score plus the residual live
target weight on secured pairs.
\end{proof}

\begin{proposition}[Activation deletion budget]\label{prop:t2-deletion-budget}
For fixed $0<\delta<1/4$, the off-model deletion count from
\Cref{prop:t2-activation-potential} satisfies
\[
  E\ll \frac{Y^4}{\log^4 Y}
  =
  o\!\left(\frac{n(\log\log n)^2}{\log n}\right).
\]
\end{proposition}

\begin{proof}
There is at most one activation round per small-prime pair, so the number of
rounds is
\[
  R\le \binom{|\mathcal P_Y|}{2}
  \ll \frac{Y^2}{\log^2Y}.
\]
We bound the number of live tokens an off-model Shortener move can delete.

If Shortener plays a large prime $b$, then for each pair $(a,c)$ there is at
most one token $acb$ using that $b$.  Hence the move deletes at most
$O(Y^2/\log^2Y)$ tokens.  If Shortener plays a lateral semiprime $pb$ with
$p\le Y$ and $b>Y$ prime, the killed targets have the form $pcb$ with the
third small prime varying, so there are at most $O(Y/\log Y)$ of them.  If
Shortener plays an exact target $acb$, exactly one token is deleted.

The worst of these bounds is the large-prime bound.  Across $R$ activation
rounds,
\[
  E\ll R\frac{Y^2}{\log^2Y}
  \ll \frac{Y^4}{\log^4Y}.
\]
Since $Y=n^\delta$,
\[
  \frac{Y^4/\log^4Y}{n(\log\log n)^2/\log n}
  \ll_\delta
  \frac{n^{4\delta-1}}{(\log n)^3(\log\log n)^2}
  \to 0
\]
because $4\delta-1<0$.
\end{proof}

\begin{proposition}[Residual mass on secured pairs]\label{prop:t2-residual-mass}
At the end of activation, the secured pairs carry residual live target weight
\[
  M:=
  \sum_{e\text{ secured}} w_{\mathrm{end}}(e)
  \gg_\delta
  \frac{n(\log\log n)^2}{\log n}.
\]
\end{proposition}

\begin{proof}
By \Cref{prop:t2-activation-potential},
\[
  S_{\mathrm{end}}+M\ge \frac{W_0}{8}-E.
\]
The activation score is at most the number of small-prime pairs:
\[
  S_{\mathrm{end}}\le R\ll \frac{Y^2}{\log^2Y}
  =
  o\!\left(\frac{n(\log\log n)^2}{\log n}\right),
\]
because $2\delta<1$.  The deletion budget $E$ is negligible by
\Cref{prop:t2-deletion-budget}, while $W_0$ has the required lower bound by
\Cref{prop:t2-initial-mass}.  Subtracting the two negligible terms gives the
claim.
\end{proof}

\begin{proposition}[Conditional T2 lower bound]\label{prop:t2-final}
Assume the restricted safe-edge hypothesis of \Cref{prop:t2-finite-capture}
for the activation graph states and for the residual slot-hypergraph states
generated by the construction above.
For every fixed $0<\delta<1/4$ there is $c_\delta>0$ such that
\[
  \L(n)\ge c_\delta\frac{n(\log\log n)^2}{\log n}
\]
for all sufficiently large $n$.
\end{proposition}

\begin{proof}
After activation, restrict to the residual live targets lying over secured
pairs.  Their total weight is $M$, as in
\Cref{prop:t2-residual-mass}.  For each secured pair $(a,c)$, the activation
move supplies a securing target $t_0(a,c)=acb_0$, and the residual subfamily
keeps only targets $acb$ with $b\ne b_0$ which remain live.  Thus the securing
target makes $a$, $c$, and $ac$ unavailable while being incomparable with every
remaining residual target over the same pair.  No other earlier move is
comparable with a residual target: Shortener's modeled activation replies are
graph vertex or edge deletions and do not produce comparable integers, while
any off-model move comparable with a target deletes that target and so removes
it from the residual live subfamily.  Therefore the strengthened hypothesis of
\Cref{prop:t2-residual-embedding} compares the remaining divisibility game to a
scored rank-$3$ slot hypergraph whose total edge weight is $M$.

Under the residual restricted safe-edge hypothesis,
\Cref{prop:t2-finite-capture} gives a strategy that forces scored residual
target weight at least $M/8$ in this hypergraph model.  The comparison
proposition says that every such scored hypergraph move is a genuine actual
game move, and that the actual game gives Prolonger no fewer legal options than
the model.  Hence the number of residual moves after activation is at least
$M/8$.  Since $M\gg_\delta n(\log\log n)^2/\log n$, the same lower bound holds
for the total game length, conditional on the restricted safe-edge hypothesis.

Choosing any fixed $\delta<1/4$, for instance $\delta=1/8$, gives an absolute
constant $c>0$ and proves \Cref{thm:t2}.
\end{proof}


\subsection{Restricted carrier classes}\label{app:restricted-carriers}

The next two propositions record unconditional upper bounds for two restricted
families of Prolonger carrier moves.  They are not used in the main upper
bound, but they clarify which carrier configurations are not responsible for
the remaining difficulty.

\begin{proposition}[Small-prime composite Prolonger with disjoint supports]
\label{prop:disjoint-carriers}
Fix $1/3<\alpha<1/2$ and put $y=n^\alpha$.  Suppose that every composite
Prolonger move has all prime factors at most $y$, and that the prime supports
of distinct composite Prolonger moves are pairwise disjoint.  Against this
restricted class, Shortener has a strategy forcing
\[
  \L(n)=O_\alpha\!\left(\frac n{\log n}\right).
\]
\end{proposition}

\begin{proof}
Shortener uses the following priority list, always skipping moves which have
already become illegal.  First, she plays every legal prime.  After this prime
phase, define $B$ to be the set of primes $p\le y$ whose singleton was not
resolved by prime play because $p$ appears in an observed composite Prolonger
carrier.  By the disjoint-support hypothesis, each $p\in B$ belongs to a
unique composite carrier $C(p)$.

Second, for every $p\in B$ whose carrier has at least two distinct prime
factors, write $e(p)=v_p(C(p))$.  If $p^{e(p)+1}\le n$, Shortener plays
$p^{e(p)+1}$.  This move is legal when it is attempted: it is not comparable
with $C(p)$, because it has a larger $p$-adic exponent while $C(p)$ contains
another prime factor; it is not comparable with any other composite carrier by
disjointness of supports; and previous priority moves either contain different
prime supports or have smaller rank.

Third, for every pair $p,q\in B$ belonging to different carriers, Shortener
plays the legal squarefree semiprime $pq$ when possible.  Such a move is
incomparable with every carrier, since no carrier contains both $p$ and $q$,
and neither $p$ nor $q$ alone is available as a legal prime at this stage.

The number of moves in the three phases is
\[
  O(\pi(n))+\pi(y)+\pi(y)^2
  =
  O_\alpha\!\left(\frac n{\log n}\right),
\]
because $2\alpha<1$.

We now show that after these phases every future legal move has no prime
factor at most $y$.  Let $x$ be a legal move divisible by a prime $p\le y$.

If $p\notin B$, then phase one either played $p$ or $p$ was already played by
Prolonger as a prime; in either case any multiple of $p$ is illegal.  Thus
$p\in B$.

If $x$ contains primes from two distinct carriers, then one of the phase-three
semiprimes $pq$ divides $x$, unless it was already illegal because an earlier
played move dividing $pq$ also divides $x$.  Either way $x$ is illegal.

Hence all prime factors of $x$ which are at most $y$ lie in a single carrier
support.  If the carrier is a pure prime power $p^e$, then any $x$ divisible by
$p$ and supported only on this carrier is another power of $p$, and is
comparable with $p^e$.  If the carrier has at least two distinct prime factors,
then either $x$ divides the carrier, in which case $x$ is illegal, or for some
$p$ it has exponent exceeding $v_p(C(p))$.  In the latter case
$p^{e(p)+1}\mid x$, so the phase-two move makes $x$ illegal.

Thus all primes $\le y$ are resolved.  Any remaining legal integer has all
prime factors greater than $y$.  Since $y^3>n$, it has at most two prime
factors.  The number of integers at most $n$ with one or two prime factors,
all exceeding $y=n^\alpha$, is $O_\alpha(n/\log n)$ by the prime number theorem
and the standard semiprime estimate
\[
  \sum_{p>y}\pi(n/p)\ll_\alpha \frac n{\log n}\sum_{p>y}\frac1p
  =O_\alpha\!\left(\frac n{\log n}\right),
\]
where the sum is over $p\le n/y$.  Adding the phase moves proves the claim.
\end{proof}

\begin{proposition}[Squarefree rank-three small-prime carriers]\label{prop:rank-three-carriers}
Fix $1/3<\alpha<1/2$ and put $y=n^\alpha$.  Suppose that every composite
Prolonger move is squarefree, has all prime factors at most $y$, and has
support size at most $3$.  Against this restricted class, Shortener has a
strategy forcing
\[
  \L(n)=O_\alpha\!\left(\frac n{\log n}\right).
\]
\end{proposition}

\begin{proof}
Let $B$ be the set of primes which occur in Prolonger's composite carriers.
Shortener again uses a fixed priority list, skipping illegal moves.

First she plays every legal prime.  Second she plays $p^2$ for every
$p\in B$ when legal.  Third she plays every legal squarefree semiprime $pq$
with $p,q\in B$.  Fourth she plays every legal squarefree triple $pqr$ with
$p,q,r\in B$.

The first phase has $O(n/\log n)$ moves, the second has at most $\pi(y)$ moves,
and the third has at most $\pi(y)^2=o(n/\log n)$ moves.  It remains to bound
the number of triples
\[
  T_\alpha(n):=\#\{p<q<r\le y:\ pqr\le n\}.
\]
Split according to whether $pq\le n^{1-\alpha}$.

If $pq\le n^{1-\alpha}$, then there are
$O(n^{1-\alpha}\log\log n/\log n)$ possible pairs $p<q$, and for each pair at
most $\pi(y)=O(n^\alpha/\log n)$ choices of $r$.  This contributes
$o(n/\log n)$.

If $pq>n^{1-\alpha}$, then $q\le y=n^\alpha$ implies
$p>n^{1-2\alpha}$.  In this range,
\[
  \#\{r:\ q<r\le y,\ pqr\le n\}
  \ll_\alpha \frac{n}{pq\log n}.
\]
Therefore the contribution is at most
\[
  \ll_\alpha
  \frac n{\log n}
  \sum_{n^{1-2\alpha}<p<q\le n^\alpha}\frac1{pq}
  =
  O_\alpha\!\left(\frac n{\log n}\right),
\]
because the reciprocal prime sum over a fixed-power interval is $O_\alpha(1)$.
Thus $T_\alpha(n)=O_\alpha(n/\log n)$.

After the prime phase, every prime $p\le y$ with $p\notin B$ has either been
played as the singleton $p$ or has had some proper multiple played; in either
case, no future legal Prolonger move can contain $p$ as a factor.  Therefore
any remaining composite Prolonger move is supported on $B$.

We prove that the priority list resolves all primes at most $y$.  After the
prime and square phases, any remaining legal move supported on $B$ must be
squarefree.  If it has support size $1$, it is comparable with a played or
blocked prime.  If it has support size $2$, then the corresponding semiprime
was either played in phase three or was already illegal because an earlier
played divisor blocks it.  If it has support size $3$, the same statement holds
for phase four.

If a remaining legal move $x$ had support size at least $4$ inside $B$, choose
three primes $p,q,r$ from its support.  The triple $pqr$ was addressed in phase
four.  If it was played, then $pqr\mid x$ and $x$ is illegal.  If it was not
legal when considered, then some earlier played move comparable with $pqr$
must divide $pqr$; since all earlier non-prime moves in the priority list have
support size at most $3$ and are squarefree except the squares $p^2$, that
played divisor also divides $x$.  Again $x$ is illegal.  Thus no remaining
legal move contains a prime at most $y$.

As in the proof of \Cref{prop:disjoint-carriers}, once all primes at most
$y$ are resolved, the residual legal set has size $O_\alpha(n/\log n)$.
Combining this residual bound with the phase counts proves the proposition.
\end{proof}
