\section{Formalization Artifact Map}\label{app:formalization}

This appendix records the status of the Lean artifacts corresponding to the
paper's principal results.  The map distinguishes between fully formalized
finite or structural cores and prose components which use standard analytic
number theory or conditional game-theoretic hypotheses.
For all entries, verification was last recorded at artifact repository tag
\texttt{arxiv-v1} (see \cite{ErdosHarness26}) and Lean toolchain
\path|leanprover/lean4:v4.28.0|.

\subsection{Verification status by result}

\begingroup
\scriptsize
\setlength{\tabcolsep}{3pt}
\renewcommand{\arraystretch}{1.18}
\begin{longtable}{>{\raggedright\arraybackslash}p{0.18\textwidth}>{\raggedright\arraybackslash}p{0.16\textwidth}>{\raggedright\arraybackslash}p{0.25\textwidth}>{\raggedright\arraybackslash}p{0.31\textwidth}}
\hline
\textbf{Result} & \textbf{Status} & \textbf{Lean file(s)} & \textbf{Notes} \\
\hline
\Cref{thm:shield-reduction} & Formally verified &
\path|shield_reduction/.../ShieldReduction.lean| &
Zero-sorry finite divisibility-poset proof. \\

\Cref{thm:theorem-A} & Partially formalized &
\path|theorem_A/.../ShieldDefs.lean|;
\path|ShieldBasicLemmas.lean|;
\path|ShieldMainTheorem.lean| &
Structural identities Lean; analytic inputs (Mertens, PNT) and assembly are prose. \\

\Cref{thm:fan-lower-bound} & Prose only &
None &
Unconditional game lower bound proved in the text; no Lean or numerical artifact is claimed. \\

\Cref{thm:t2} & Conditional; finite cores Lean-verified &
\path|T2Finite/GraphGame.lean|;
\path|T2Finite/HyperGame.lean|;
\path|T2Finite/ResidualComparison.lean| &
Conditional on the restricted safe-edge hypothesis.  The safe-edge hypothesis and asymptotic activation wrapper remain prose. \\

\Cref{thm:five-twenty-four} & Formally verified &
\path|tau_5_24/.../Cover.lean|;
\path|Packing.lean|;
\path|Tau.lean| &
Cover and packing identities are zero-sorry Lean; the final floor-sum asymptotic is elementary prose. \\

\Cref{thm:thirteen-thirtysix} & Formally verified &
\path|shortener_13_36/.../Compression.lean|;
\path|Sieve.lean|;
\path|MainTheorem.lean| &
Zero-sorry odd-part compression and Bonferroni core; standard prime-prefix estimates are used in the prose setup. \\

\Cref{thm:five-sixteen} & Partially formalized &
\path|shortener_5_16/.../Defs.lean|;
\path|Theorems.lean| &
Compression, sieve, and algebraic optimization are Lean-checked; one placeholder bundles Chebyshev prime-prefix input and the game-tree prefix wrapper. \\

\Cref{thm:main-upper} & Partially formalized &
\path|Round15Bonferroni4/Target.lean| &
Lean covers the endgame reduction in \path|Round15Bonferroni4/Target.lean|; envelope, inversion, measure convergence, and prime-rounding bridge are prose. \\

\Cref{thm:prime-bridge} & Prose only &
None &
The queued prime-rounding bridge is proved in \Cref{sec:main-upper}; no separate Lean artifact is claimed. \\

\Cref{prop:wfour-certification} & Prose with numerical stress testing &
\path|scripts/wfour_certification.py| &
Outward-rounded interval certificate computes the four displayed $J_r$ intervals and the final margin. \\

\Cref{prop:sa-barrier} & Prose with numerical stress testing &
\path|scripts/sa_barrier_verification.py| &
Proof is prose; the script exhaustively checks the lifted covering inequalities for small $N$ with exact rational arithmetic. \\

\Cref{prop:q-shadow-dichotomy} & Prose only &
None &
Extremal shadow argument is presented in the text; no artifact is claimed. \\

\Cref{prop:separator-only} & Prose only &
None &
Arithmetic closure limitation is presented in the text; no artifact is claimed. \\
\hline
\end{longtable}
\endgroup

\begingroup
\scriptsize
\medskip
\noindent\textbf{Shield Reduction, \Cref{thm:shield-reduction}.}\par
Path: \path|erdos-872/lean/shield_reduction/shield_reduction_aristotle/RequestProject/ShieldReduction.lean|.
Declarations: \path|shield_reduction|.
Status: zero-sorry Lean verification; no remaining assumptions beyond the
finite definitions of the divisibility poset.

\medskip
\noindent\textbf{Exact $5/24$ cover, \Cref{thm:five-twenty-four}.}\par
Path: \path|erdos-872/lean/tau_5_24/tau_5_24_aristotle/RequestProject/Tau.lean|.
Declarations: \path|coverSet_is_cover| and \path|cover_card_lower_bound|.
Status: the structural cover and packing identities are zero-sorry
Lean-verified; the asymptotic floor-sum count $5n/24+O(1)$ is an elementary
prose calculation.

\medskip
\noindent\textbf{$13/36$ upper bound, \Cref{thm:thirteen-thirtysix}.}\par
Path: \path|erdos-872/lean/shortener_13_36/shortener_13_36_v2_aristotle/RequestProject/Shortener/MainTheorem.lean|.
Declarations: \path|antichain_dfree_bound| and \path|main_upper_bound|.
Status: the odd-part compression and Bonferroni core are zero-sorry
Lean-verified; the paper-level exposition uses standard prime-counting estimates
for the prime-prefix setup.

\medskip
\noindent\textbf{Polynomial shield-weight lower bound, \Cref{thm:theorem-A}.}\par
Path: \path|erdos-872/lean/theorem_A/theorem_A_shield_lower_bound_aristotle/RequestProject/ShieldMainTheorem.lean|.
Declarations: \path|shield_lower_bound| and \path|barrier_exponent|.
Status: the combinatorial core, including the prime-antichain construction,
log-budget argument, and exchange principle, has a Lean artifact.  Remaining
sorries are Mertens' theorem, a Chebyshev-type prime-counting bound, a
Chebyshev-$\vartheta$ asymptotic, and the final assembly using those analytic
inputs.

\medskip
\noindent\textbf{$5/16$ upper bound, \Cref{thm:five-sixteen}.}\par
Path: \path|erdos-872/lean/shortener_5_16/shortener_5_16_aristotle/RequestProject/Shortener516/Theorems.lean|.
Declarations: \path|antichain_three_five_core_bound|,
\path|game_value_per_parameter|, and \path|main_theorem|.
Status: the compression, sieve, and algebraic optimization core has a Lean
artifact.  One remaining bundled placeholder covers the Chebyshev prime-prefix
estimate and the game-tree wrapper realizing the prescribed prefix.

\medskip
\noindent\textbf{Conditional T2 lower bound, \Cref{thm:t2}.}\par
Paths:
\begin{lstlisting}[basicstyle=\ttfamily\scriptsize,breaklines=true,breakatwhitespace=false,columns=fullflexible]
erdos-872/lean/erdos_872_core/RequestProject/T2Finite/GraphGame.lean
erdos-872/lean/erdos_872_core/RequestProject/T2Finite/HyperGame.lean
erdos-872/lean/erdos_872_core/RequestProject/T2Finite/ResidualComparison.lean
\end{lstlisting}
Declarations:
\begin{lstlisting}[basicstyle=\ttfamily\scriptsize,breaklines=true,breakatwhitespace=false,columns=fullflexible]
Q8_maker_ge_add_selfPot
HQ8_maker_ge_add_selfPot_of_count_le_two
comparison_package
\end{lstlisting}
Status: the finite graph-potential core, scored hypergraph core, and local
arithmetic embedding core are Lean-verified.  The restricted safe-edge
hypothesis is conditional, and the asymptotic activation wrapper remains in
prose.

\medskip
\noindent\textbf{Main $0.19n$ upper bound, \Cref{thm:main-upper}.}\par
Path:
\begin{lstlisting}[basicstyle=\ttfamily\scriptsize,breaklines=true,breakatwhitespace=false,columns=fullflexible]
erdos-872/lean/erdos_872_core/RequestProject/Round15Bonferroni4/Target.lean
\end{lstlisting}
Declaration:
\begin{lstlisting}[basicstyle=\ttfamily\scriptsize,breaklines=true,breakatwhitespace=false,columns=fullflexible]
eventually_strict_lt_point19_of_componentwise_close
\end{lstlisting}
Status: the endgame reduction from sufficiently close first-four moment values
to the strict inequality $\L(n)<0.19n$ is zero-sorry Lean-verified.  The local
density theorem, monotone envelope and inversion, and prime-rounding bridge are
the prose moment-convergence inputs proved in \Cref{sec:main-upper}.
\endgroup

This map should be read conservatively.  A zero-sorry finite core is not being
advertised as an end-to-end verification of every analytic asymptotic in the
same theorem unless the entry says so explicitly.  Conversely, when the
remaining obligations are standard analytic-number-theory inputs, the novelty
of the combinatorial argument is already isolated in the formal artifact.
