\section{Numerical Computations}\label{app:numerical}

This appendix records the numerical computations accompanying the main
Bonferroni--4 constant.  The computations certify the quoted constants and
stress-test the finite combinatorial steps, but they are not substitutes for
the analytic proof in \Cref{sec:main-upper}.

\subsection{The Bonferroni--4 constant}

The main theorem uses the following certified upper bound.

\begin{proposition}[Interval-arithmetic certification of $\Wfour/2<0.19$]
\label{prop:wfour-certification}
For the moment constants in \Cref{sec:main-upper},
\[
\begin{aligned}
  J_1&\in[0.7885305658,\,0.7885305661],\\
  J_2&\in[0.18681848,\,0.18682451],\\
  J_3&\in[0.02009209,\,0.02009370],\\
  J_4&\in[0.00122263,\,0.00122282].
\end{aligned}
\]
Consequently
\[
  \frac{\Wfour}{2}\le 0.1897123371<0.19.
\]
In particular one may take a numerical margin
$\eta=2.87\cdot10^{-4}$ in $\Wfour/2\le0.19-\eta$.
\end{proposition}

\begin{proof}
Let $\mu(du)=\rhoU(u)\,du$.  Then
\[
  r!J_r
  =
  \mu^{\otimes r}\{(u_1,\ldots,u_r):u_1+\cdots+u_r\le1\}.
\]
Take $N=10^5$ and partition $(0,1]$ into
\[
  I_i=\left(\frac{i-1}{N},\frac{i}{N}\right]\qquad(1\le i\le N).
\]
Write $m_i=\mu(I_i)$.  These masses are computed from an exact antiderivative:
if $x\in(1/(h+1),1/h]$, then
\[
  F(x):=\int_0^x\rhoU(u)\,du
  =
  T_{h+1}+\frac{1}{h+1}\log((h+1)x),
\]
where
\[
  T_k:=\sum_{\ell=k}^{\infty}\frac{\log(1+1/\ell)}{\ell+1}.
\]
Thus $m_i=F(i/N)-F((i-1)/N)$.  For certification the tails $T_k$ are truncated
at $H^\star=10^6$.  Since
\[
  \frac{1}{(\ell+1)^2}
  \le
  \frac{\log(1+1/\ell)}{\ell+1}
  \le
  \frac{1}{\ell(\ell+1)},
\]
we have
\[
  \sum_{\ell>H^\star}\frac{\log(1+1/\ell)}{\ell+1}
  \le
  \sum_{\ell>H^\star}\frac{1}{\ell(\ell+1)}
  =
  \frac{1}{H^\star+1}.
\]
All logarithms, sums, differences, and products are evaluated with
outward-rounded interval arithmetic.  A reference Python implementation using
\texttt{mpmath.iv} for the interval cell masses is available at
\texttt{scripts/wfour\_certification.py} in the artifact repository
\cite{ErdosHarness26}.  Running it with the default parameters computes the cell
masses by splitting grid cells at the exact breakpoints $1/h$, performs the
four interval convolutions with an explicit FFT round-off enclosure, and
reproduces intervals contained in the certified intervals displayed above.

Let $c_s^{(r)}$ be the interval convolution coefficients
\[
  c_s^{(r)}
  :=
  \sum_{i_1+\cdots+i_r=s}m_{i_1}\cdots m_{i_r}.
\]
Every product cell with $i_1+\cdots+i_r\le N$ lies wholly inside the simplex,
while every product cell which can meet the simplex satisfies
$(i_1-1)+\cdots+(i_r-1)\le N$, equivalently
$i_1+\cdots+i_r\le N+r$.  Therefore
\[
  \frac1{r!}\sum_{s\le N}c_s^{(r)}
  \le
  J_r
  \le
  \frac1{r!}\sum_{s\le N+r}c_s^{(r)}.
\]
The upper condition $s\le N+r$ is a harmless overcount of one convolution
shell relative to the exact meeting condition $s\le N+r-1$; the displayed
upper bounds are therefore slightly looser than sharp but remain rigorous.
Carrying out these outward-rounded interval convolutions gives the four
intervals displayed above.  Finally, using the lower endpoints for $J_1,J_3$
and the upper endpoints for $J_2,J_4$,
\[
  \frac{\Wfour}{2}
  \le
  \frac12(1-0.7885305658+0.18682451-0.02009209+0.00122282)
  =
  0.1897123371<0.19.
\]
\end{proof}

\subsection{Directed-rounding implementation details}

The certification in \Cref{prop:wfour-certification} uses only standard
outward-rounded interval operations.  The implementation may use IEEE-754
directed rounding modes, or a library with documented correctly rounded
elementary functions.  For each positive input $x$, compute lower and upper
logarithms
\[
  \log_{\rm dn}(x)\le \log x\le \log_{\rm up}(x).
\]
All lower partial sums are accumulated with round-down arithmetic, and all
upper partial sums with round-up arithmetic.  If an interval antiderivative
value is written $F(x)\in[F_{\rm dn}(x),F_{\rm up}(x)]$, then the cell mass
$m_i=F(i/N)-F((i-1)/N)$ is enclosed by
\[
\begin{aligned}
  m_i^-&=\operatorname{round}_{\rm dn}
  \bigl(F_{\rm dn}(i/N)-F_{\rm up}((i-1)/N)\bigr),\\
  m_i^+&=\operatorname{round}_{\rm up}
  \bigl(F_{\rm up}(i/N)-F_{\rm dn}((i-1)/N)\bigr).
\end{aligned}
\]
The convolution coefficients $c_s^{(r)}$ are then enclosed by interval
polynomial multiplication.  A direct implementation may round each product and
each accumulated partial sum outward.  The reference script uses an FFT
accelerator, but encloses its floating-point round-off by an explicit
$\ell^1$-error bound for each convolution and propagates that bound through the
later products.  Concretely, for a Cooley--Tukey FFT of transform length $L$
and nonnegative inputs $a,b$ with $\ell^1$-norms $\|a\|_1,\|b\|_1$, the script
bounds the total $\ell^1$ round-off error in the computed $a*b$ by
\begin{equation}\label{eq:fft-l1-bound}
  256\cdot\varepsilon_{\rm mach}\cdot
  (\lceil\log_2 L\rceil+1)^2\cdot\|a\|_1\|b\|_1,
\end{equation}
where $\varepsilon_{\rm mach}$ is the IEEE-754 double-precision machine
epsilon.  This form dominates the standard $\gamma_k$ error model of
Higham~\cite[Chapter~24]{Higham02} applied to the two forward transforms, the
pointwise multiplication, and the inverse transform; the constant $256$ is an
intentionally conservative safety factor.  The bound
\eqref{eq:fft-l1-bound} is added outward to the computed convolution, and the
widened interval is used in all downstream products.  Thus the displayed
certification does not rely on an unbounded floating-point FFT error model.

A direct grid computation of the same integrals gives the convergence displayed
in \Cref{tab:grid-bonferroni}.  The theorem only needs the certified strict
margin below $0.19$, while the table records an independent convergence check.
\[
  J_r=
  \frac1{r!}
  \int_{\substack{u_1+\cdots+u_r\le1\\0<u_i\le1}}
  \prod_{i=1}^r \rho(u_i)\,du_1\cdots du_r
\]
is the quantity being approximated.

\begin{table}[ht]
\centering
\small
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
Grid & $J_1$ & $J_2$ & $J_3$ & $J_4$ & $\Wfour$ & $\Wfour/2$ \\
\hline
$2^{13}$ & 0.78844185 & 0.18676003 & 0.02008041 & 0.00122154 & 0.37945930 & 0.18972965 \\
$2^{14}$ & 0.78849100 & 0.18679383 & 0.02008737 & 0.00122220 & 0.37943767 & 0.18971883 \\
$2^{15}$ & 0.78851725 & 0.18681153 & 0.02009097 & 0.00122255 & 0.37942586 & 0.18971293 \\
$2^{16}$ & 0.78852127 & 0.18681405 & 0.02009149 & 0.00122260 & 0.37942388 & 0.18971194 \\
$2^{17}$ & 0.78852704 & 0.18681777 & 0.02009220 & 0.00122266 & 0.37942118 & 0.18971059 \\
\hline
\end{tabular}
\caption{Grid convergence for the Bonferroni--4 truncation.}
\label{tab:grid-bonferroni}
\end{table}

\subsection{Finite sanity checks}

Four finite checks were used to guard against implementation or formulation
errors in the proof.

\begin{enumerate}
  \item \emph{Odd-part injection.}  Exhaustive verification at $n=14$ over all
  $732$ antichains found no collision under the odd-part map.
  \item \emph{Monotone replacement.}  Exact inclusion--exclusion counts at
  $n=10^4,10^5,10^6$ for test prime pairs $(q_j)$ and $(p_j)$ with
  $q_j\le p_j$ confirmed $N(q_1,\ldots,q_K)\le N(p_1,\ldots,p_K)$.
  \item \emph{Squarefree divisor counts.}  For $r\le4$, the relevant
  squarefree $r$-fold divisor counts match the scale
  $O_r(n(\log\log n)^{r-1}/\log n)$ used in the Bonferroni floor-error bound.
  \item \emph{Controlled prime rounding.}  Synthetic monotone comparison
  prefixes were rounded upward to increasing odd-prime prefixes at
  $n=10^4,10^5,10^6,10^8$; the resulting changes in the moment terms were
  small and consistent with the prime-rounding bridge.
\end{enumerate}

\begin{table}[ht]
\centering
\small
\begin{tabular}{|l|l|}
\hline
Check & Recorded outcome \\
\hline
Odd-part injection & \texttt{(True, None, None, 732)} at $n=14$ \\
Monotone replacement & Verified at $n=10^4,10^5,10^6$ for listed test prefixes \\
$D_r$ scaling & Ratified for $r=1,2,3,4$ up to $n=10^6$ \\
Prime-rounding bridge & Tested on synthetic prefixes up to $n=10^8$ \\
\hline
\end{tabular}
\caption{Finite checks for the combinatorial components of the upper-bound proof.}
\label{tab:finite-checks}
\end{table}

\subsection{Interpretation}

The numerical artifacts support three claims: the constant $\Wfour/2<0.19$ is
reproducible; the finite steps in \Cref{thm:bonf-comp,thm:prime-bridge} behave
as expected in representative regimes; and the sharper limiting value near
$0.18969$ is numerically stable.  The theorem in this paper is the finite
Bonferroni--4 bound below $0.19$, not a claim that the full alternating series
has been analytically justified.

\subsection{Reproducibility}

From the repository root, the certificate is reproduced by running
\[
  \texttt{python3 scripts/wfour\_certification.py}.
\]
The default parameters are $N=10^5$, $H^\star=10^6$, and $80$ decimal digits;
no flags are needed to reproduce intervals contained in the displayed
certified intervals.  The script imports only the Python standard library,
\texttt{mpmath}, and \texttt{numpy}; the run used for this manuscript was tested
with Python~3.14.3, \texttt{mpmath}~1.3.0, and \texttt{numpy}~2.4.2 on macOS
Darwin~25.2.0 (arm64).  No separate stdout transcript is archived in the
repository; running the command prints a self-describing block containing the
four $J_r$ intervals, the final $\Wfour/2$ interval, the margin to $0.19$, and
the elapsed wall-clock time.
